---
title: "The effect of attention and working memory on the estimation of elapsed time"
author: "Ignacio Polti"
date: "July 23, 2018"
output: html_document
---


# Libraries
***
```{r}
library(ggplot2)
library(grid)
library(gridExtra)
library(car)
library(lme4)
library(lmerTest)
library(lmtest)
library(betareg)
library(fitdistrplus)
library(multcomp)
library(lsmeans)
library(visreg)
```
<br><br>


# Paths
```{r}
DT_Fdbck_path <- file.path("home.ansatt.ntnu.no",
                           "ignatiop",
                           "Documents",
                           "UNICOG",
                           "M1_thesis",
                           "Data_original_sample")
ST_Fdbck_path <- file.path("home.ansatt.ntnu.no",
                           "ignatiop",
                           "Documents",
                           "UNICOG",
                           "M1_thesis",
                           "Data_original_sample")
DT_NoFdbck_path <- file.path("home.ansatt.ntnu.no",
                             "ignatiop",
                             "Documents",
                             "UNICOG",
                             "M1_thesis",
                             "Data_ctrl_sample")
ST_NoFdbck_path <- file.path("home.ansatt.ntnu.no",
                             "ignatiop",
                             "Documents",
                             "UNICOG",
                             "M1_thesis",
                             "Data_ctrl_sample")
```
<br><br>


# Colorblind-friendly palettes
***
```{r}
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442",
               "#0072B2", "#D55E00", "#CC79A7")
cbPalette2 <- c("#0072B2", "#CC79A7")
cbPalette2_v2 <- c("#66c2a4", "#fc8d59")
cbPalette3 <- c("#009E73", "#0072B2", "#CC79A7")
cbPalette4 <- c("#E69F00", "#56B4E9", "#009E73", "#D55E00", "#CC79A7")

qualiPalette3 <- c("#66c2a5", "#fc8d62", "#8da0cb")
qualiPalette3_v2 <- c("#a6cee3", "#1f78b4", "#b2df8a")
qualiPalette3_v3 <- c("#fc8d59", "#ffffbf", "#91bfdb")

cbPaletteCTRL_DT <- c(rep("#d7b5d8", 5), "#bdc9e1", rep("#df65b0", 5),
                      "#74a9cf", rep("#ce1256", 5), "#0570b0")

cbPaletteST0back <- c("#0072B2", "#bdbdbd")

```
<br><br>


# Functions
***
## Extract plot legend
```{r}
get_legend <- function(myggplot){
  tmp <- ggplot_gtable(ggplot_build(myggplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}
```
## Load & merge data files
```{r}
# == Load all Dual Task data files =============================================
# ==============================================================================
multmerge_DT = function(mypath){
  filenames = list.files(path = mypath,
                         full.names = TRUE,
                         pattern = 'DT')
  datalist = lapply(filenames, function(x){read.table(file = x,
                                                      header = TRUE)})
  Reduce(function(x, y) {merge(x, y, all = TRUE)}, datalist)}

# == Load all Single Task data files ===========================================
# ==============================================================================
multmerge_ST = function(mypath){
  filenames = list.files(path = mypath,
                         full.names = TRUE,
                         pattern = 'ST')
  datalist = lapply(filenames, function(x){read.table(file = x,
                                                      header = TRUE)})
  Reduce(function(x,y) {merge(x, y, all = TRUE)}, datalist)}
```
## Standard Error of the Mean (SEM)
```{r}
sem <- function(x){sd(x)/sqrt(length(x))}
```
## Outliers removal
```{r}
remove_outliers <- function(x, na.rm = TRUE, ...) {
qnt <- quantile(x, probs = c(.25, .75), na.rm = na.rm, ...)
H <- 1.5 * IQR(x, na.rm = na.rm)
Y <- x
Y[x < (qnt[1] - H)] <- NA
Y[x > (qnt[2] + H)] <- NA
Y}
```
## A' (Signal Detection Theory)
```{r}
A_prime <- function(H, F) {
  if (F <= .5 & H >= .5)
  {
    a <- .75 + (H - F)/4 - F*(1 - H)
  } else if (F <= H & H <= .5)
  {
    a <- .75 + (H - F)/4 - F/(4*H)
  } else {
      a <- .75 + (H - F)/4 - (1 - H)/(4*(1 - F))
  } 
  return(a)}
```
## B'' (Signal Detection Theory)
```{r}
Bppd <- function(H, F) {
  if (F <= .5 & H >= .5)
  {
    b <- (5 - 4*H)/(1 + 4*F)
  }
  else if (F <= H & H <= .5)
  {
    b <- (H^2 + H)/(H^2 + F)
  } else {
      b <- ((1 - F)^2 + (1 - H)/(1 - F^2) + (1 - F))
  } 
  return(b)}
```
## d' (Signal Detection Theory)
```{r}
dprime <- function(H, F) {qnorm(H) - qnorm(F)}
```
## Beta (Signal Detection Theory)
```{r}
Beta <- function(H, F) {zhr <- qnorm(H)
```
<br><br>


# Data cleansing
***
```{r}
# == Dataset construction ======================================================
# ==============================================================================
dataset_DT.Fdbck <- multmerge_DT(DT_Fdbck_path)
dataset_ST.Fdbck <- multmerge_ST(ST_Fdbck_path)
dataset_DT.NoFdbck <- multmerge_DT(DT_NoFdbck_path)
dataset_ST.NoFdbck <- multmerge_ST(ST_NoFdbck_path)

# == Dual Task | Feedback trials ===============================================
# ==============================================================================
# Change factor's names
colnames(dataset_DT.Fdbck)[6] <- "INTERVAL"
colnames(dataset_DT.Fdbck)[12] <- "ESTIMATE"
colnames(dataset_DT.Fdbck)[2] <- "SUBJ_ID"

# Set specific columns as "factor" data types
dataset_DT.Fdbck$Nro_SUBJ <- as.factor(dataset_DT.Fdbck$Nro_SUBJ)
dataset_DT.Fdbck$RUN <- as.factor(dataset_DT.Fdbck$RUN)
dataset_DT.Fdbck$BLOCK <- as.factor(dataset_DT.Fdbck$BLOCK)
dataset_DT.Fdbck$BACK <- as.factor(dataset_DT.Fdbck$BACK)

dataset_DT.Fdbck$INTERVAL <- dataset_DT.Fdbck$INTERVAL/1000
dataset_DT.Fdbck$RT < -as.numeric(as.character(dataset_DT.Fdbck$RT))
dataset_DT.Fdbck$ESTIMATE <- as.numeric(as.character(dataset_DT.Fdbck$ESTIMATE))
dataset_DT.Fdbck$COUNTER <- NULL
dataset_DT.Fdbck$STIM <- NULL
dataset_DT.Fdbck$Norm_Est <- dataset_DT.Fdbck$ESTIMATE - dataset_DT.Fdbck$INTERVAL
dataset_DT.Fdbck$INTERVAL <- as.factor(dataset_DT.Fdbck$INTERVAL)
dataset_DT.Fdbck$COND <- "Fdbck"
dataset_DT.Fdbck$COND <- as.factor(dataset_DT.Fdbck$COND)
levels(dataset_DT.Fdbck$ANSWER)[levels(dataset_DT.Fdbck$ANSWER) == "None"] <- "CRej"
dataset_DT.Fdbck$TRIAL <- gsub("T_ESTIMATE", "T_EST", dataset_DT.Fdbck$TRIAL)


# == Single Task | Feedback trials =============================================
# ==============================================================================
# Change factor's names
colnames(dataset_ST.Fdbck)[4] <- "INTERVAL"
colnames(dataset_ST.Fdbck)[6] <- "ESTIMATE"
colnames(dataset_ST.Fdbck)[2] <- "SUBJ_ID"

dataset_ST.Fdbck$Nro_SUBJ <- as.factor(dataset_ST.Fdbck$Nro_SUBJ)
dataset_ST.Fdbck$INTERVAL <- dataset_ST.Fdbck$INTERVAL/1000
dataset_ST.Fdbck$RT <- as.numeric(as.character(dataset_ST.Fdbck$RT))
dataset_ST.Fdbck$ESTIMATE <- as.numeric(as.character(dataset_ST.Fdbck$ESTIMATE))
dataset_ST.Fdbck$Norm_Est <- dataset_ST.Fdbck$ESTIMATE - dataset_ST.Fdbck$INTERVAL
dataset_ST.Fdbck$INTERVAL <- as.factor(dataset_ST.Fdbck$INTERVAL)
dataset_ST.Fdbck$TRIAL <-  NULL
dataset_ST.Fdbck$COND <- "Fdbck"
dataset_ST.Fdbck$COND <- as.factor(dataset_ST.Fdbck$COND)
dataset_ST.Fdbck$TASK <- "ST"
dataset_ST.Fdbck$TASK <- as.factor(dataset_ST.Fdbck$TASK)
dataset_ST.Fdbck <- dataset_ST.Fdbck[c('Nro_SUBJ', 'SUBJ_ID', 'TASK', 
                                       'INTERVAL', 'RT', 'ESTIMATE',
                                       'Norm_Est', 'COND')]


# == Dual Task | No Feedback trials ============================================
# ==============================================================================
dataset_DT.NoFdbck$SEX[dataset_DT.NoFdbck$SEX == "FALSE"] <- "Female"
dataset_DT.NoFdbck$SEX[dataset_DT.NoFdbck$SEX == "M"] <- "Male"
colnames(dataset_DT.NoFdbck)[10] <- "INTERVAL"
colnames(dataset_DT.NoFdbck)[16] <- "ESTIMATE"
dataset_DT.NoFdbck$Nro_SUBJ <- as.factor(dataset_DT.NoFdbck$Nro_SUBJ)
dataset_DT.NoFdbck$RUN <- as.factor(dataset_DT.NoFdbck$RUN)
dataset_DT.NoFdbck$BLOCK <- as.factor(dataset_DT.NoFdbck$BLOCK)

dataset_DT.NoFdbck$BACK <- as.factor(dataset_DT.NoFdbck$BACK)
dataset_DT.NoFdbck$INTERVAL <- dataset_DT.NoFdbck$INTERVAL/1000
dataset_DT.NoFdbck$ESTIMATE <- as.numeric(as.character(dataset_DT.NoFdbck$ESTIMATE))
dataset_DT.NoFdbck$Norm_Est <- dataset_DT.NoFdbck$ESTIMATE - dataset_DT.NoFdbck$INTERVAL
dataset_DT.NoFdbck$INTERVAL <- as.factor(dataset_DT.NoFdbck$INTERVAL)

dataset_DT.NoFdbck$RT <- as.numeric(as.character(dataset_DT.NoFdbck$RT))
dataset_DT.NoFdbck$COUNTER <- NULL
dataset_DT.NoFdbck$TIME <- NULL
dataset_DT.NoFdbck$DATE <- NULL
dataset_DT.NoFdbck$AGE <- NULL
dataset_DT.NoFdbck$STIM <- NULL
dataset_DT.NoFdbck$COND <- "NoFdbck"
dataset_DT.NoFdbck$COND <- as.factor(dataset_DT.NoFdbck$COND)

# == Single Task | No Feedback trials ==========================================
# ==============================================================================
dataset_ST.NoFdbck$COUNTER <- NULL
dataset_ST.NoFdbck$TIME <- NULL
dataset_ST.NoFdbck$DATE <- NULL
dataset_ST.NoFdbck$AGE <- NULL
dataset_ST.NoFdbck$SEX[dataset_ST.NoFdbck$SEX == "FALSE"] <- "Female"
dataset_ST.NoFdbck$SEX[dataset_ST.NoFdbck$SEX == "M"] <- "Male"
colnames(dataset_ST.NoFdbck)[7] <- "INTERVAL"
colnames(dataset_ST.NoFdbck)[12] <- "ESTIMATE"
colnames(dataset_ST.NoFdbck)[6] <- "TASK"
dataset_ST.NoFdbck$TASK <- "ST"
dataset_ST.NoFdbck$Nro_SUBJ <- as.factor(dataset_ST.NoFdbck$Nro_SUBJ)
dataset_ST.NoFdbck$RUN <- as.factor(dataset_ST.NoFdbck$RUN)
dataset_ST.NoFdbck$BLOCK <- as.factor(dataset_ST.NoFdbck$BLOCK)
dataset_ST.NoFdbck$TASK <- as.factor(dataset_ST.NoFdbck$TASK)
dataset_ST.NoFdbck$INTERVAL <- dataset_ST.NoFdbck$INTERVAL/1000
dataset_ST.NoFdbck$RT <- as.numeric(as.character(dataset_ST.NoFdbck$RT))
dataset_ST.NoFdbck$ESTIMATE <- as.numeric(as.character(dataset_ST.NoFdbck$ESTIMATE))
dataset_ST.NoFdbck$Norm_Est <- dataset_ST.NoFdbck$ESTIMATE - dataset_ST.NoFdbck$INTERVAL
dataset_ST.NoFdbck$INTERVAL <- as.factor(dataset_ST.NoFdbck$INTERVAL)
dataset_ST.NoFdbck$TRIAL <- NULL
dataset_ST.NoFdbck$STIM <- NULL
dataset_ST.NoFdbck$ANSWER <- NULL
dataset_ST.NoFdbck$COND <- "NoFdbck"
dataset_ST.NoFdbck$COND <- as.factor(dataset_ST.NoFdbck$COND)
```
<br><br>


# Merge datasets by trial-type (DT / ST)
***
```{r}
dataset_DT <- dataset_DT.NoFdbck
dataset_DT$SEX <- NULL
dataset_DT <- rbind(dataset_DT, dataset_DT.Fdbck)

dataset_ST <- dataset_ST.NoFdbck
dataset_ST$SEX <- NULL
dataset_ST$RUN <- NULL
dataset_ST$BLOCK <- NULL
dataset_ST <- rbind(dataset_ST, dataset_ST.Fdbck)
```
<br><br>


# Separate prospective / retrospective timing trials
```{r}
# == Retrospective timing ======================================================
# ==============================================================================
retrospectiveT_data <- subset(dataset_DT, RUN == 0 & BLOCK == 1)


# == Prospective timing ========================================================
# ==============================================================================
prospectiveT_data <- subset(dataset_DT, RUN != 0 | BLOCK != 1)
```
<br><br>


# n-back task Dependent Variables (DV)
***
## Signal Detection Theory (SDT): Hit Rate (HR) | False Alarm rate (FA)
```{r}
# == Pre-compute SDT variables =================================================
# ==============================================================================
nback_DV <- subset(prospectiveT_data, TRIAL != 'T_EST')
nback_DV$ESTIMATE <- NULL
nback_DV$Norm_Est <- NULL

true_sbset <- subset(nback_DV, ANSWER == "True")
miss_sbset <- subset(nback_DV, ANSWER == "Miss")
false_sbset <- subset(nback_DV, ANSWER == "False")
crej_sbset <- subset(nback_DV, ANSWER == "CRej")

true.n <- aggregate(true_sbset$ANSWER,
                    by = list(Nro_SUBJ = true_sbset$Nro_SUBJ,
                              RUN = true_sbset$RUN,
                              BLOCK = true_sbset$BLOCK,
                              BACK = true_sbset$BACK,
                              INTERVAL = true_sbset$INTERVAL,
                              CONDITION = true_sbset$COND),
                    drop = FALSE,
                    length)

miss.n <- aggregate(miss_sbset$ANSWER,
                    by = list(Nro_SUBJ = miss_sbset$Nro_SUBJ,
                              RUN = miss_sbset$RUN,
                              BLOCK = miss_sbset$BLOCK,
                              BACK = miss_sbset$BACK,
                              INTERVAL = miss_sbset$INTERVAL,
                              CONDITION = miss_sbset$COND),
                    drop = FALSE,
                    length)

false.n <- aggregate(false_sbset$ANSWER,
                     by = list(Nro_SUBJ = false_sbset$Nro_SUBJ,
                               RUN = false_sbset$RUN,
                               BLOCK = false_sbset$BLOCK,
                               BACK = false_sbset$BACK,
                               INTERVAL = false_sbset$INTERVAL,
                               CONDITION = false_sbset$COND),
                     drop = FALSE,
                     length)

crej.n <- aggregate(crej_sbset$ANSWER,
                    by = list(Nro_SUBJ = crej_sbset$Nro_SUBJ,
                              RUN = crej_sbset$RUN,
                              BLOCK = crej_sbset$BLOCK,
                              BACK = crej_sbset$BACK,
                              INTERVAL = crej_sbset$INTERVAL,
                              CONDITION = crej_sbset$COND),
                    drop = FALSE,
                    length)

pre_sdt <- true.n
names(pre_sdt)[names(pre_sdt) == "x"] <- "True"
pre_sdt$Miss <- miss.n$x
pre_sdt$False <- false.n$x
pre_sdt$CRej <- crej.n$x
pre_sdt[is.na(pre_sdt)] <- 0
pre_sdt$H <- pre_sdt$True/(pre_sdt$True + pre_sdt$Miss)
pre_sdt$F <- pre_sdt$False/(pre_sdt$False + pre_sdt$CRej)
sdt_DV <- pre_sdt[complete.cases(pre_sdt[, 11]),]

sdt_DV$H.crt <- sdt_DV$H
sdt_DV$H.crt[(sdt_DV$H == 1)] <- 1 - (1/(2*sdt_DV$True[sdt_DV$H == 1]))
sdt_DV$H.crt[(sdt_DV$H == 0)] <- 1/(2*sdt_DV$Miss[sdt_DV$H == 0])

sdt_DV$F.crt <- sdt_DV$F
sdt_DV$F.crt[(sdt_DV$F == 1)] <- 1 - (1/(2*sdt_DV$False[sdt_DV$F == 1]))
sdt_DV$F.crt[(sdt_DV$F == 0)] <- 1/(2*sdt_DV$CRej[sdt_DV$F == 0])

# A' and B'' calculation:

#A' original calculation

# A_prime<- function(H, F) {a<- 1/2 + ((H-F)*(1+H-F) / (4*H*(1-F)))
# b<- 1/2 - ((F-H)*(1+F-H) / (4*F*(1-H)))
# a[F>H]<-b[F>H]
# a[F==H]<-.5
# a}

# Bppd <- function(H,F) {((1-H)*(1-F)-H*F) / ((1-H)*(1-F)+H+F)}


#A' and b corrected calculation (Zhang & Mueller, 2005)


zfar <- qnorm(F)
exp(-zhr*zhr/2 + zfar*zfar/2)}

sdt_DV$A_prime <- A_prime(sdt_DV$H.crt, sdt_DV$F.crt)
sdt_DV$B_ppd <- Bppd(sdt_DV$H.crt, sdt_DV$F.crt)
sdt_DV$d_prime <- dprime(sdt_DV$H.crt, sdt_DV$F.crt)
sdt_DV$beta <- Beta(sdt_DV$H.crt, sdt_DV$F.crt)
```

## Response Time (RT)
```{r}
nback.rt <- subset(prospectiveT_data, TRIAL != 'T_EST')
nback.rt$ESTIMATE <- NULL
nback.rt$Norm_Est <- NULL

# == Early responses (RT < 100) ================================================
# ==============================================================================
earlyRT.count.T <- subset(nback_DV, RT < 100 & ANSWER == 'True')
earlyRT.count.F <- subset(nback_DV, RT < 100 & ANSWER == 'False')

earlyRT.false <- aggregate(earlyRT.count.F$RT,
                           by = list(BACK = earlyRT.count.F$BACK,
                                     INTERVAL = earlyRT.count.F$INTERVAL,
                                     CONDITION = earlyRT.count.F$COND),
                           sd)
earlyRT.false.n <- aggregate(earlyRT.count.F$RT,
                             by = list(BACK = earlyRT.count.F$BACK,
                                       INTERVAL = earlyRT.count.F$INTERVAL,
                                       CONDITION = earlyRT.count.F$COND),
                             length)
names(earlyRT.false)[names(earlyRT.false) == "x"] <- "SD"
earlyRT.false$LENGTH <- earlyRT.false.n$x

# == Accurate target responses =================================================
# ==============================================================================
nback.rt.F <- subset(nback.rt, ANSWER == "False" & RT > 100)
nback.rt.T <- subset(nback.rt, ANSWER == "True" & RT > 100)

nback.rt.T <- aggregate(nback.rt.T$RT,
                        by = list(Nro_SUBJ = nback.rt.T$Nro_SUBJ,
                                  RUN = nback.rt.T$RUN,
                                  BLOCK = nback.rt.T$BLOCK,
                                  BACK = nback.rt.T$BACK,
                                  INTERVAL = nback.rt.T$INTERVAL,
                                  CONDITION = nback.rt.T$COND),
                        mean)
```

## Merge SDT + RT DV
```{r}
nback.bhvr <- merge(nback.rt.T,
                    sdt_DV,
                    all = TRUE)
names(nback.bhvr)[names(nback.bhvr) == "x"] <- "RT"
```
<br><br>


# Behavioral measurements (Figure 1c)
***
## HR
```{r}
# == Pre-compute HR variables ==================================================
# ==============================================================================
HR.wmload.fdbck <- aggregate(nback.bhvr$H.crt,
                             by = list(BACK = nback.bhvr$BACK,
                                       COND = nback.bhvr$CONDITION),
                             mean)
HR.wmload.fdbck.sd <- aggregate(nback.bhvr$H.crt,
                                by = list(BACK = nback.bhvr$BACK,
                                          COND = nback.bhvr$CONDITION),
                                sd)
HR.wmload.fdbck.n <- aggregate(nback.bhvr$H.crt,
                               by = list(BACK = nback.bhvr$BACK,
                                         COND = nback.bhvr$CONDITION),
                               length)
names(HR.wmload.fdbck)[names(HR.wmload.fdbck) == "x"] <- "MEAN"
HR.wmload.fdbck$SD <- HR.wmload.fdbck.sd$x
HR.wmload.fdbck$N <- HR.wmload.fdbck.n$x
HR.wmload.fdbck$SEM <- HR.wmload.fdbck$SD / sqrt(HR.wmload.fdbck$N)
```
### Sub-figure
```{r}
hr_noS_BW <- ggplot(data = HR.wmload.fdbck,
                    aes(x = BACK, y = MEAN, group = COND)) + 
  geom_errorbar(aes(ymin = MEAN - SEM, ymax = MEAN + SEM),
                width = .1, 
                show.legend = FALSE,
                size = 1) +
  geom_line(aes(group = COND, linetype = COND), size = 1.5) +
  geom_point(size = 2, 
             show.legend = FALSE) +
  labs(x = "Working Memory load", 
       y = "Hit Rate") +
  scale_x_discrete(limits = c("0", "1", "2", "3"), 
                   labels = c("0", "1", "2", "3")) +
  scale_y_continuous(breaks = seq(from = .3, to = 1, by = .1)) +
  expand_limits(y = c(.3, 1)) +
  theme_classic() +
  theme(legend.position = c(.25, .1),
        legend.title = element_text(face = "bold", size = 18), 
        legend.text = element_text(size = 15),
        axis.line.x = element_line(color = "black", size = .5),
        axis.line.y = element_line(color = "black", size = .5),
        plot.title = element_text(size = 18, face = "bold"),
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 18)) +
  scale_linetype_manual(values = c(1, 3),
                        name = "Condition",
                        labels = c("No Feedback", "Feedback"))
```

## FA
```{r}
# == Pre-compute FA variables ==================================================
# ==============================================================================
FA.wmload.fdbck <- aggregate(nback.bhvr$F.crt,
                             by = list(BACK = nback.bhvr$BACK,
                                       COND = nback.bhvr$CONDITION),
                             mean)
FA.wmload.fdbck.sd <- aggregate(nback.bhvr$F.crt,
                                by = list(BACK = nback.bhvr$BACK,
                                          COND = nback.bhvr$CONDITION),
                                sd)
FA.wmload.fdbck.n <- aggregate(nback.bhvr$F.crt,
                               by = list(BACK = nback.bhvr$BACK,
                                         COND = nback.bhvr$CONDITION),
                               length)
names(FA.wmload.fdbck)[names(FA.wmload.fdbck) == "x"] <- "MEAN"
FA.wmload.fdbck$SD <- FA.wmload.fdbck.sd$x
FA.wmload.fdbck$N <- FA.wmload.fdbck.n$x
FA.wmload.fdbck$SEM <- FA.wmload.fdbck$SD / sqrt(FA.wmload.fdbck$N)
```
### Sub-figure
```{r}
fa_noS_BW <- ggplot(data = FA.wmload.fdbck,
                    aes(x = BACK, y = MEAN, group = COND)) + 
  geom_errorbar(aes(ymin = MEAN - SEM,
                    ymax = MEAN + SEM),
                width = .1,
                size = 1) +
  geom_line(aes(group = COND, linetype = COND), size = 1.5) +
  geom_point(size = 2) +
  labs(x = "Working Memory load", 
       y = "False Alarm Rate") +
  scale_x_discrete(limits = c("0", "1", "2", "3"), 
                   labels = c("0", "1", "2", "3")) +
  scale_y_continuous(breaks = seq(from = 0, to = .08, by = .01)) + 
  expand_limits(y = c(0, .08)) +
  theme_classic() +
  theme(legend.position = "none",
        legend.title = element_text(face = "bold", size = 18), 
        legend.text = element_text(size = 15),
        axis.line.x = element_line(color = "black", size = .5),
        axis.line.y = element_line(color = "black", size = .5),
        plot.title = element_text(size = 18, face = "bold"),
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 18)) +
  scale_linetype_manual(values = c(1, 3))
```

## RT
```{r}
# == Pre-compute RT variables ==================================================
# ==============================================================================
pre_RT.wmload.fdbck <- nback.bhvr[complete.cases(nback.bhvr[, 7]),]
RT.wmload.fdbck <- aggregate(pre_RT.wmload.fdbck$RT,
                             by = list(BACK = pre_RT.wmload.fdbck$BACK,
                                       COND = pre_RT.wmload.fdbck$CONDITION),
                             mean)
RT.wmload.fdbck.sd <- aggregate(pre_RT.wmload.fdbck$RT,
                                by = list(BACK = pre_RT.wmload.fdbck$BACK,
                                          COND = pre_RT.wmload.fdbck$CONDITION),
                                sd)
RT.wmload.fdbck.n <- aggregate(pre_RT.wmload.fdbck$RT,
                               by = list(BACK = pre_RT.wmload.fdbck$BACK,
                                         COND = pre_RT.wmload.fdbck$CONDITION),
                               length)
names(RT.wmload.fdbck)[names(RT.wmload.fdbck) == "x"] <- "MEAN"
RT.wmload.fdbck$SD <- RT.wmload.fdbck.sd$x
RT.wmload.fdbck$N <- RT.wmload.fdbck.n$x
RT.wmload.fdbck$SEM <- RT.wmload.fdbck$SD / sqrt(RT.wmload.fdbck$N)
```
## Sub-figure
```{r}
pd1 <- position_dodge(0.1)
rt_noS_BW <- ggplot(data = RT.wmload.fdbck,
                    aes(x = BACK,
                        y = MEAN,
                        group = COND)) +
  geom_errorbar(aes(ymin = MEAN - SEM, ymax = MEAN + SEM), 
                width = .1,  
                show.legend = FALSE,
                size = 1) +
  geom_line(aes(group = COND, linetype = COND), size = 1.5) +
  geom_point(size = 2) +
  labs(x = "Working Memory load", 
       y = "Mean Reaction Time (ms)") +
  scale_x_discrete(limits = c("0", "1", "2", "3"), 
                   labels = c("0", "1", "2", "3")) +
  theme_classic() +
  theme(legend.title = element_text(face = "bold", size = 18), 
        legend.text = element_text(size = 15), 
        legend.position = "none",
        plot.title = element_text(size = 18, face = "bold"),
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 18)) +
  scale_y_continuous(breaks = seq(from = 400, to = 700, by = 30), 
                     limits = c(400, 700)) +
  scale_linetype_manual(values = c(1, 3))
```

## Joint figure
```{r}
f0 <- grid.arrange(hr_noS_BW, fa_noS_BW, rt_noS_BW,
                   ncol = 3,
                   nrow = 1, 
                   widths = c(.5, .5, .5))

# Save image
ggsave(f0,
       file = "D:/M1_thesis/analysis/f0.svg",
       dpi = 700)
```
<br><br>


# Subjective duration estimation: Outliers removal
***
```{r}
# == ST | SUBJECTIVE DURATION ==================================================
# ==============================================================================
clean_ST.data <- dataset_ST

clean_ST.data$ESTIMATE <- remove_outliers(dataset_ST$ESTIMATE)
clean_ST.data <- clean_ST.data[complete.cases(clean_ST.data[, 6]),]
clean_ST.data$RT <- remove_outliers(clean_ST.data$RT)
clean_ST.data <- clean_ST.data[complete.cases(clean_ST.data[, 5]),]

# == ST | SUBJECTIVE DURATION DEVIATION ========================================
# ==============================================================================
clean_STdev.data <- dataset_ST

clean_STdev.data$Norm_Est <- remove_outliers(dataset_ST$Norm_Est)
clean_STdev.data <- clean_STdev.data[complete.cases(clean_STdev.data[, 7]),]
clean_STdev.data$RT <- remove_outliers(clean_STdev.data$RT)
clean_STdev.data <- clean_STdev.data[complete.cases(clean_STdev.data[, 5]),]

# == DT | SUBJECTIVE DURATION ==================================================
# ==============================================================================
clean_DT.Time_data <- subset(prospectiveT_data, TRIAL == "T_EST")
clean_DT.data <- clean_DT.Time_data

clean_DT.data$ESTIMATE <- remove_outliers(clean_DT.Time_data$ESTIMATE)
clean_DT.data <- clean_DT.data[complete.cases(clean_DT.data[, 10]),]
clean_DT.data$RT <- remove_outliers(clean_DT.data$RT)
clean_DT.data <- clean_DT.data[complete.cases(clean_DT.data[, 9]),]

# == DT | SUBJECTIVE DURATION DEVIATION ========================================
# ==============================================================================
clean_DTdev.Time_data <- subset(prospectiveT_data, TRIAL == "T_EST")
clean_DTdev.data <- clean_DTdev.Time_data

clean_DTdev.data$Norm_Est <- remove_outliers(clean_DTdev.Time_data$Norm_Est)
clean_DTdev.data <- clean_DTdev.data[complete.cases(clean_DTdev.data[, 11]),]
clean_DTdev.data$RT <- remove_outliers(clean_DTdev.data$RT)
clean_DTdev.data <- clean_DTdev.data[complete.cases(clean_DTdev.data[, 9]),]
```
<br><br>


# Subjective duration deviation x Feedback x WM load
***
```{r}
# == ST | WM load x Target Duration x Feedback =================================
# ==============================================================================
clean_STdev.data_norm <- clean_STdev.data
names(clean_STdev.data_norm)[names(clean_STdev.data_norm) == "TASK"] <- "WMLOAD"
clean_STdev_ag <- aggregate(clean_STdev.data_norm$Norm_Est,
                            by = list(WMLOAD = clean_STdev.data_norm$WMLOAD,
                                      INTERVAL = clean_STdev.data_norm$INTERVAL, 
                                      COND = clean_STdev.data_norm$COND), mean)
clean_STdev_ag.x <- aggregate(clean_STdev.data_norm$Norm_Est,
               by = list(WMLOAD = clean_STdev.data_norm$WMLOAD,
                         INTERVAL = clean_STdev.data_norm$INTERVAL,
                         COND = clean_STdev.data_norm$COND), median)
clean_STdev_ag.y <- aggregate(clean_STdev.data_norm$Norm_Est,
               by = list(WMLOAD = clean_STdev.data_norm$WMLOAD, 
                         INTERVAL = clean_STdev.data_norm$INTERVAL, 
                         COND = clean_STdev.data_norm$COND), sd)
clean_STdev_ag.z <- aggregate(clean_STdev.data_norm$Norm_Est,
               by = list(WMLOAD = clean_STdev.data_norm$WMLOAD, 
                         INTERVAL = clean_STdev.data_norm$INTERVAL,
                         COND = clean_STdev.data_norm$COND), length)

names(clean_STdev_ag)[names(clean_STdev_ag) == "x"] <- "MEAN"
clean_STdev_ag$MEDIAN <- clean_STdev_ag.x$x
clean_STdev_ag$SD <- clean_STdev_ag.y$x
clean_STdev_ag$N <- clean_STdev_ag.z$x
clean_STdev_ag$SEM <- clean_STdev_ag$SD / sqrt(clean_STdev_ag$N)

# == DT | WM load x Target Duration x Feedback =================================
# ==============================================================================
clean_DTdev_ag <- aggregate(clean_DTdev.data$Norm_Est,
                            by = list(WMLOAD = clean_DTdev.data$BACK,
                                      INTERVAL = clean_DTdev.data$INTERVAL, 
                                      COND = clean_DTdev.data$COND), mean)
clean_DTdev_ag.x <- aggregate(clean_DTdev.data$Norm_Est,
               by = list(WMLOAD = clean_DTdev.data$BACK,
                         INTERVAL = clean_DTdev.data$INTERVAL,
                         COND = clean_DTdev.data$COND), median)
clean_DTdev_ag.y <- aggregate(clean_DTdev.data$Norm_Est,
               by = list(WMLOAD = clean_DTdev.data$BACK, 
                         INTERVAL = clean_DTdev.data$INTERVAL, 
                         COND = clean_DTdev.data$COND), sd)
clean_DTdev_ag.z <- aggregate(clean_DTdev.data$Norm_Est,
               by = list(WMLOAD = clean_DTdev.data$BACK, 
                         INTERVAL = clean_DTdev.data$INTERVAL,
                         COND = clean_DTdev.data$COND), length)

names(clean_DTdev_ag)[names(clean_DTdev_ag) == "x"] <- "MEAN"
clean_DTdev_ag$MEDIAN <- clean_DTdev_ag.x$x
clean_DTdev_ag$SD <- clean_DTdev_ag.y$x
clean_DTdev_ag$N <- clean_DTdev_ag.z$x
clean_DTdev_ag$SEM <- clean_DTdev_ag$SD / sqrt(clean_DTdev_ag$N)

# == Bind ST | DT ==============================================================
# ==============================================================================
clean_ST.DTdev_data <- rbind(clean_STdev_ag, clean_DTdev_ag)
clean_ST.DTdev_data$WMLOAD <- factor(clean_ST.DTdev_data$WMLOAD,
                                     levels = c("ST", "0", "1", "2", "3"))
# = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = 


# == ST | WM load x Target Duration ============================================
# ==============================================================================
clean_STdev.data_norm2 <- clean_STdev.data
names(clean_STdev.data_norm2)[names(clean_STdev.data_norm2) == "TASK"] <- "WMLOAD"
clean_STdev_ag2 <- aggregate(clean_STdev.data_norm2$Norm_Est,
                             by = list(WMLOAD = clean_STdev.data_norm2$WMLOAD,
                                       INTERVAL = clean_STdev.data_norm2$INTERVAL),
                             mean)
clean_STdev_ag2.x <- aggregate(clean_STdev.data_norm2$Norm_Est,
                               by = list(WMLOAD = clean_STdev.data_norm2$WMLOAD,
                                         INTERVAL = clean_STdev.data_norm2$INTERVAL),
                               median)
clean_STdev_ag2.y <- aggregate(clean_STdev.data_norm2$Norm_Est,
                               by = list(WMLOAD = clean_STdev.data_norm2$WMLOAD,
                                         INTERVAL = clean_STdev.data_norm2$INTERVAL),
                               sd)
clean_STdev_ag2.z <- aggregate(clean_STdev.data_norm2$Norm_Est,
                               by = list(WMLOAD = clean_STdev.data_norm2$WMLOAD,
                                         INTERVAL = clean_STdev.data_norm2$INTERVAL),
                               length)

names(clean_STdev_ag2)[names(clean_STdev_ag2) == "x"] <- "MEAN"
clean_STdev_ag2$MEDIAN <- clean_STdev_ag2.x$x
clean_STdev_ag2$SD <- clean_STdev_ag2.y$x
clean_STdev_ag2$N <- clean_STdev_ag2.z$x
clean_STdev_ag2$SEM <- clean_STdev_ag2$SD / sqrt(clean_STdev_ag2$N)

# == DT | WM load x Target Duration ============================================
# ==============================================================================
clean_DTdev_ag1 <- clean_DTdev.data
clean_DTdev_ag1$BACK <- "DT"
clean_DTdev_ag1$BACK <- as.factor(clean_DTdev_ag1$BACK)
clean_DTdev_ag2 <- aggregate(clean_DTdev_ag1$Norm_Est,
                             by = list(WMLOAD = clean_DTdev_ag1$BACK,
                                       INTERVAL = clean_DTdev_ag1$INTERVAL), 
                             mean)
clean_DTdev_ag2.x <- aggregate(clean_DTdev_ag1$Norm_Est,
                               by = list(WMLOAD = clean_DTdev_ag1$BACK,
                                         INTERVAL = clean_DTdev_ag1$INTERVAL),
                               median)
clean_DTdev_ag2.y <- aggregate(clean_DTdev_ag1$Norm_Est,
                               by = list(WMLOAD = clean_DTdev_ag1$BACK, 
                                         INTERVAL = clean_DTdev_ag1$INTERVAL),
                               sd)
clean_DTdev_ag2.z <- aggregate(clean_DTdev_ag1$Norm_Est,
                               by = list(WMLOAD = clean_DTdev_ag1$BACK, 
                                         INTERVAL = clean_DTdev_ag1$INTERVAL), 
                               length)

names(clean_DTdev_ag2)[names(clean_DTdev_ag2) == "x"] <- "MEAN"
clean_DTdev_ag2$MEDIAN <- clean_DTdev_ag2.x$x
clean_DTdev_ag2$SD <- clean_DTdev_ag2.y$x
clean_DTdev_ag2$N <- clean_DTdev_ag2.z$x
clean_DTdev_ag2$SEM <- clean_DTdev_ag2$SD / sqrt(clean_DTdev_ag2$N)

# == Bind ST | DT ==============================================================
# ==============================================================================
clean_ST.DTdev_data2 <- rbind(clean_STdev_ag2, clean_DTdev_ag2)
clean_ST.DTdev_data2$WMLOAD <- factor(clean_ST.DTdev_data2$WMLOAD,
                                      levels = c("ST", "DT"))
# = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = 


# == ST vs DT[0-back] | DEV DATA ===============================================
# ==============================================================================
clean_0back.dev_ag3 <- subset(clean_DTdev.data, BACK == "0")
clean_0back_ag4 <- aggregate(clean_0back.dev_ag3$Norm_Est,
                             by = list(WMLOAD = clean_0back.dev_ag3$BACK,
                                       INTERVAL = clean_0back.dev_ag3$INTERVAL), 
                             mean)
clean_0back_ag4.x <- aggregate(clean_0back.dev_ag3$Norm_Est,
                               by = list(WMLOAD = clean_0back.dev_ag3$BACK,
                                         INTERVAL = clean_0back.dev_ag3$INTERVAL),
                               median)
clean_0back_ag4.y <- aggregate(clean_0back.dev_ag3$Norm_Est,
                               by = list(WMLOAD = clean_0back.dev_ag3$BACK, 
                                         INTERVAL = clean_0back.dev_ag3$INTERVAL),
                               sd)
clean_0back_ag4.z <- aggregate(clean_0back.dev_ag3$Norm_Est,
                               by = list(WMLOAD = clean_0back.dev_ag3$BACK, 
                                         INTERVAL = clean_0back.dev_ag3$INTERVAL), 
                               length)

names(clean_0back_ag4)[names(clean_0back_ag4) == "x"] <- "MEAN"
clean_0back_ag4$MEDIAN <- clean_0back_ag4.x$x
clean_0back_ag4$SD <- clean_0back_ag4.y$x
clean_0back_ag4$N <- clean_0back_ag4.z$x
clean_0back_ag4$SEM <- clean_0back_ag4$SD / sqrt(clean_0back_ag4$N)

# == Bind ST | DT[0-back] ======================================================
# ==============================================================================
clean_ST.0back.dev_data <- rbind(clean_STdev_ag2, clean_0back_ag4)
clean_ST.0back.dev_data$WMLOAD <- factor(clean_ST.0back.dev_data$WMLOAD,
                                         levels = c("ST", "0"))
```
## Figures
```{r}
# == ST vs DT | Feedback | WM load =============================================
# ==============================================================================
pd <- position_dodge(0.3)
f1 <- ggplot(data = clean_ST.DTdev_data, aes(x = WMLOAD,
                                             y = MEAN,
                                             group = INTERVAL,
                                             colour = interaction(INTERVAL,
                                                                  WMLOAD))) +
  geom_hline(aes(yintercept = 0), 
             colour = 'black', 
             size = .5, 
             linetype = "dashed") +
  geom_vline(aes(xintercept = 2), 
             colour = 'black', 
             size = .5) +
  geom_errorbar(aes(ymin = MEAN - SEM, ymax = MEAN + SEM), 
                width = .1,
                position = pd, 
                show.legend = FALSE) + 
  geom_point(size = 5, 
             position = pd) + 
  labs(x = "Working Memory load", y = "Subjective duration deviation (s)") +
  scale_x_discrete(limits = c("ST", "", "0", "1", "2", "3"), 
                   labels = c("Empty\ninterval", "", "0", "1", "2", "3")) + 
  coord_fixed(ratio = .2) + 
  guides(size = FALSE) + 
  scale_y_continuous(breaks = seq(from = -25, to = 25, by = 5),
                     limits = c(-25, 25)) + 
  theme_classic() + 
  geom_line(data = subset(clean_ST.DTdev_data, WMLOAD != "ST"), 
            aes(colour = INTERVAL), 
            size = 1.5, 
            show.legend = FALSE,
            position = pd) + 
  theme(legend.title = element_text(face = "bold", size = 18),
        legend.text = element_text(size = 15), 
        axis.text = element_text(size = 18),
        axis.title = element_text(size = 18),
        strip.background = element_blank(),
        strip.text = element_text(size = 20, face = "bold"),
        panel.spacing = unit(2, "lines")) +
  scale_colour_manual(values = cbPaletteCTRL_DT,
                      name = "Duration",
                      labels = c("30s Single task",
                                 "60s Single task",
                                 "90s Single task",
                                 "30s Dual task",
                                 "60s Dual task",
                                 "90s Dual task"),
                      breaks = c("30.ST", "60.ST", "90.ST", "30", "60", "90")) +
  facet_grid(~COND)

# Save image
ggsave(f1,
       file = "D:/M1_thesis/analysis/f1.svg",
       dpi = 700)


# == ST vs DT | Target duration ================================================
# ==============================================================================
STvs0back2$INTERVAL <- as.numeric(as.character(STvs0back2$INTERVAL))
f2 <- ggplot(data = clean_ST.DTdev_data2, aes(x = INTERVAL,
                                              y = MEAN,
                                              group = WMLOAD,
                                              colour = WMLOAD)) +
  labs(x = "Objective duration (s)", y = "Subjective duration deviation (s)") +
  scale_y_continuous(breaks = seq(from = -15, to = 10, by = 2),
                     limits = c(-15, 10)) +
  geom_hline(aes(yintercept = 0), 
             colour = 'black', 
             size = .5, 
             linetype = "dashed") +
  theme_classic() +
  theme(legend.title = element_blank(),
  legend.text = element_text(size = 15),
  legend.position = c(.2, .1),
  axis.title = element_text(size = 18),
  axis.text = element_text(size = 18),
  strip.background = element_blank(),
  strip.text = element_text(size = 20, face = "bold"),
  panel.spacing = unit(2, "lines")) +
  geom_errorbar(aes(ymin = MEAN - SEM, ymax = MEAN + SEM),
                colour = "black",
                width = .05,
                show.legend = FALSE) +
  geom_point(size = 3) +
  geom_line(aes(group = WMLOAD), 
            size = 2,
            show.legend = FALSE) +
  scale_fill_manual(values = cbPalette2,
                    labels = c("Single task",
                               "Dual task")) +
  scale_colour_manual(values = cbPalette2,
                      labels = c("Single task",
                                 "Dual task"))

# Save image
ggsave(f2,
       file = "D:/M1_thesis/analysis/f2.svg",
       dpi = 700)


# == ST vs DT[0-back] | Target duration ========================================
# ==============================================================================
f3 <- ggplot(data = clean_ST.0back.dev_data, aes(x = INTERVAL,
                                                 y = MEAN,
                                                 group = WMLOAD,
                                                 colour = WMLOAD)) +
  labs(x = "Objective duration (s)", y = "Subjective duration deviation (s)") +
  scale_y_continuous(breaks = seq(from = -15, to = 10, by = 2),
                     limits = c(-15, 10)) +
  geom_hline(aes(yintercept = 0), 
             colour = 'black', 
             size = .5, 
             linetype = "dashed") +
  theme_classic() +
  theme(legend.title = element_blank(),
  legend.text = element_text(size = 15),
  legend.position = c(.2, .1),
  axis.title = element_text(size = 18),
  axis.text = element_text(size = 18),
  strip.background = element_blank(),
  strip.text = element_text(size = 20, face = "bold"),
  panel.spacing = unit(2, "lines")) +
  geom_errorbar(aes(ymin = MEAN - SEM, ymax = MEAN + SEM),
                colour = "black",
                width = .05,
                show.legend = FALSE) +
  geom_point(size = 3) +
  geom_line(aes(group = WMLOAD), 
            size = 2,
            show.legend = FALSE) +
  scale_fill_manual(values = cbPaletteST0back,
                    labels = c("Single task",
                               "Dual task: 0-back")) +
  scale_colour_manual(values = cbPaletteST0back,
                      labels = c("Single task",
                                 "Dual task: 0-back"))

# Save image
ggsave(f3,
       file = "D:/M1_thesis/analysis/f3.svg",
       dpi = 700)
```
<br><br>


# Merged ST-dev / DT
***
```{r}
# == Prepare dataset ===========================================================
# ==============================================================================
pre_merged_ST <- clean_STdev.data
pre_merged_ST$RT <- NULL
names(pre_merged_ST)[names(pre_merged_ST) == "TASK"] <- "WMLOAD"

pre_merged_DT <- clean_DT.data
pre_merged_DT$RT <- NULL
pre_merged_DT$RUN <- NULL
pre_merged_DT$BLOCK <- NULL
pre_merged_DT$ANSWER <- NULL
pre_merged_DT$TRIAL <- NULL
names(pre_merged_DT)[names(pre_merged_DT) == "BACK"] <- "WMLOAD"
merged_ST.DT <- rbind(pre_merged_ST, pre_merged_DT)
```

## ST vs DT[0-back] | CV (Figure 2a, inset)
```{r}
# == Pre-compute descriptive stats =============================================
# ==============================================================================
clean_0back_cv <- subset(merged_ST.DT, WMLOAD == "0" | WMLOAD == "ST")
clean_0back_cv_avg <- aggregate(clean_0back_cv$ESTIMATE,
                                by = list(SUBJ = clean_0back_cv$SUBJ_ID,
                                          WMLOAD = clean_0back_cv$WMLOAD,
                                          INTERVAL = clean_0back_cv$INTERVAL),
                                mean)

clean_0back_cv_avg.sd <- aggregate(clean_0back_cv$ESTIMATE,
                                   by = list(SUBJ = clean_0back_cv$SUBJ_ID,
                                             WMLOAD = clean_0back_cv$WMLOAD,
                                             INTERVAL = clean_0back_cv$INTERVAL),
                                   sd)

clean_0back_cv_avg.length <- aggregate(clean_0back_cv$ESTIMATE,
                                       by = list(SUBJ = clean_0back_cv$SUBJ_ID,
                                                 WMLOAD = clean_0back_cv$WMLOAD,
                                                 INTERVAL = clean_0back_cv$INTERVAL),
                                       length)

names(clean_0back_cv_avg)[names(clean_0back_cv_avg) == "x"] <- "MEAN"
clean_0back_cv_avg$SD <- clean_0back_cv_avg.sd$x
clean_0back_cv_avg$N <- clean_0back_cv_avg.length$x
clean_0back_cv_avg$CV <- clean_0back_cv_avg$SD / clean_0back_cv_avg$MEAN
clean_0back_cv_avg <- clean_0back_cv_avg[complete.cases(clean_0back_cv_avg[, 7]),]

# == ST vs DT[0-back] | Averaged CV ============================================
# ==============================================================================
clean_0back_cv_avg2 <- aggregate(clean_0back_cv_avg$CV,
                                 by = list(WMLOAD = clean_0back_cv_avg$WMLOAD,
                                           INTERVAL = clean_0back_cv_avg$INTERVAL),
                                 mean)

clean_0back_cv_avg2.sd <- aggregate(clean_0back_cv_avg$CV,
                                    by = list(WMLOAD = clean_0back_cv_avg$WMLOAD,
                                              INTERVAL = clean_0back_cv_avg$INTERVAL),
                                    sd)

clean_0back_cv_avg2.length <- aggregate(clean_0back_cv_avg$CV,
                                        by = list(WMLOAD = clean_0back_cv_avg$WMLOAD,
                                                  INTERVAL = clean_0back_cv_avg$INTERVAL),
                                        length)

names(clean_0back_cv_avg2)[names(clean_0back_cv_avg2) == "x"] <- "MEAN"
clean_0back_cv_avg2$SD <- clean_0back_cv_avg2.sd$x
clean_0back_cv_avg2$N <- clean_0back_cv_avg2.length$x
clean_0back_cv_avg2$SEM <- clean_0back_cv_avg2$SD / sqrt(clean_0back_cv_avg2$N)
```
## Figure
```{r}
pd <- position_dodge(0.1)
f4 <- ggplot(data = clean_0back_cv_avg2, aes(x = INTERVAL,
                                             y = MEAN,
                                             group = WMLOAD,
                                             colour = WMLOAD)) +
  labs(y = "CV") +
  scale_y_continuous(breaks = seq(from = .125, to = .250, by = .025),
                     limits = c(.125, .250)) +
  theme_classic() +
  theme(legend.position = "none",
  axis.title = element_text(size = 18),
  axis.text = element_text(size = 18),
  axis.title.x = element_blank(),
  strip.background = element_blank(),
  strip.text = element_text(size = 20, face = "bold"),
  panel.spacing = unit(2, "lines")) +
  geom_errorbar(aes(ymin = MEAN - SEM, ymax = MEAN + SEM),
                colour = "black",
                width = .05,
                show.legend = FALSE,
                position = pd) +
  geom_point(size = 4,
             position = pd) +
  geom_line(aes(group = WMLOAD), 
            size = 2,
            show.legend = FALSE,
            position = pd) +
  scale_fill_manual(values = cbPaletteST0back) +
  scale_colour_manual(values = cbPaletteST0back)

# Save image
ggsave(f4,
       file = "D:/M1_thesis/analysis/f4.svg",
       dpi = 700)
```
<br><br>


# ST vs DT[0-back] | SUBJECTIVE DURATION DEVIATION (Figure 2a)
***
```{r}
# == Pre-compute descriptive stats =============================================
# ==============================================================================
clean_0back <- subset(merged_ST.DT, WMLOAD == "0")
clean_0back_avg <- aggregate(clean_0back$Norm_Est,
                             by = list(WMLOAD = clean_0back$WMLOAD,
                                       INTERVAL = clean_0back$INTERVAL), 
                             mean)
clean_0back_avg.sd <- aggregate(clean_0back$Norm_Est,
                             by = list(WMLOAD = clean_0back$WMLOAD,
                                       INTERVAL = clean_0back$INTERVAL), 
                             sd)
clean_0back_avg.length <- aggregate(clean_0back$Norm_Est,
                             by = list(WMLOAD = clean_0back$WMLOAD,
                                       INTERVAL = clean_0back$INTERVAL), 
                             length)

names(clean_0back_avg)[names(clean_0back_avg) == "x"] <- "MEAN"
clean_0back_avg$SD <- clean_0back_avg.sd$x
clean_0back_avg$N <- clean_0back_avg.length$x
clean_0back_avg$SEM <- clean_0back_avg$SD / sqrt(clean_0back_avg$N)

clean_STdev_ag3 <- clean_STdev_ag2
clean_STdev_ag3$MEDIAN <- NULL
clean_0back_avg <- rbind(clean_STdev_ag3, clean_0back_avg)
```
## Figure
```{r}
f5 <- ggplot(data = clean_0back_avg, aes(x = INTERVAL,
                                         y = MEAN,
                                         group = WMLOAD,
                                         colour = WMLOAD)) +
  labs(x = "Objective duration (s)", y = "Subjective duration deviation (s)") +
  scale_y_continuous(breaks = seq(from = -10, to = 10, by = 2),
                     limits = c(-10, 10)) +
  geom_hline(aes(yintercept = 0), 
             colour = 'black', 
             size = .5, 
             linetype = "dashed") +
  theme_classic() +
  theme(legend.title = element_blank(),
  legend.text = element_text(size = 15),
  legend.position = c(.2, .95),
  axis.title = element_text(size = 18),
  axis.text = element_text(size = 18),
  strip.background = element_blank(),
  strip.text = element_text(size = 20, face = "bold"),
  panel.spacing = unit(2, "lines")) +
  geom_errorbar(aes(ymin = MEAN - SEM, ymax = MEAN + SEM),
                colour = "black",
                width = .05,
                show.legend = FALSE) +
  geom_point(size = 3) +
  geom_line(aes(group = WMLOAD), 
            size = 2,
            show.legend = FALSE) +
  scale_fill_manual(values = cbPaletteST0back,
                    labels = c("Single task",
                               "Dual task: 0-back")) +
  scale_colour_manual(values = cbPaletteST0back,
                      labels = c("Single task",
                                 "Dual task: 0-back"))

# Save image
ggsave(f5,
       file = "D:/M1_thesis/analysis/f5.svg",
       dpi = 700)
```
<br><br>


# ST vs DT | SUBJECTIVE DURATION | SCATTER PLOT (Figure 2b)
***
```{r}
# == Pre-compute descriptive stats =============================================
# ==============================================================================
DT_sel <- pre_merged_DT
DT_sel$WMLOAD <- "DT"
DT_sel$WMLOAD <- as.factor(DT_sel$WMLOAD)
merged_ST.DT_sel <- rbind(pre_merged_ST, DT_sel)

merged_ST.DT_sel2 <- merged_ST.DT_sel
merged_ST.DT_sel_avgT <- aggregate(merged_ST.DT_sel$ESTIMATE,
                                   by = list(WMLOAD = merged_ST.DT_sel$WMLOAD,
                                             INTERVAL = merged_ST.DT_sel$INTERVAL),
                                   mean)
names(merged_ST.DT_sel_avgT)[names(merged_ST.DT_sel_avgT) == "x"] <- "MEAN"
```
## Figure
```{r}
merged_ST.DT_sel2$INTERVAL <- as.numeric(as.character(merged_ST.DT_sel2$INTERVAL))
merged_ST.DT_sel_avgT$INTERVAL <- as.numeric(as.character(merged_ST.DT_sel_avgT$INTERVAL))

pd <- position_dodge(6)
f6 <- ggplot(data = merged_ST.DT_sel2, aes(x = INTERVAL,
                                           y = ESTIMATE,
                                           group = WMLOAD,
                                           colour = WMLOAD)) +
  geom_segment(aes(x = 0, y = 0, xend = 150, yend = 150),
               colour = 'black',
               linetype = "dashed") +
  geom_point(position = pd, alpha = .5) +
  geom_line(data = merged_ST.DT_sel_avgT,
            aes(x = INTERVAL, y = MEAN, group = WMLOAD, colour = WMLOAD),
            position = pd,
            size = 2,
            show.legend = FALSE) +
  geom_point(data = merged_ST.DT_sel_avgT,
             aes(x = INTERVAL,
                 y = MEAN,
                 group = WMLOAD,
                 colour = WMLOAD),
             size = 4,
             position = pd) +
  labs(x = "Objective duration (s)", y = "Subjective duration (s)") +
  scale_y_continuous(breaks = seq(from = 0, to = 150, by = 30),
                     labels = c(0, 30, 60, 90, 120, 150)) +
  scale_x_continuous(breaks = seq(from = 30, to = 90, by = 30),
                     labels = c(30, 60, 90)) +
  coord_cartesian(xlim = c(0, 120), ylim = c(0, 150)) +
  theme_classic() +
  theme(legend.position = c(.15, .9), 
        legend.title = element_blank(),
        legend.text = element_text(size = 18), 
        axis.line.x = element_line(color = "black", size = .5),
        axis.line.y = element_line(color = "black", size = .5),
        axis.title = element_text(size = 20),
        axis.text = element_text(size = 20)) +
  scale_fill_manual(values = cbPalette2, 
                    labels = c("Single task", "Dual task")) +
  scale_colour_manual(values = cbPalette2, 
                      labels = c("Single task", "Dual task"))

# Save image
ggsave(f6,
       file = "D:/M1_thesis/analysis/f6.svg",
       dpi = 700)
```
<br><br>


# ST vs DT | VARIANCE (Figure 2c)
***
```{r}
# == Pre-compute descriptive stats =============================================
# ==============================================================================
var_ST.DT <- aggregate(merged_ST.DT_sel$ESTIMATE,
                       by = list(SUBJ = merged_ST.DT_sel$SUBJ_ID,
                              WMLOAD = merged_ST.DT_sel$WMLOAD,
                              INTERVAL = merged_ST.DT_sel$INTERVAL,
                              COND = merged_ST.DT_sel$COND),
                       var)

names(var_ST.DT)[names(var_ST.DT) == "x"] <- "VAR"
var_ST.DT <- var_ST.DT[complete.cases(var_ST.DT[, 5]),]

var_ST.DT.mean <- aggregate(var_ST.DT$VAR,
                            by = list(WMLOAD = var_ST.DT$WMLOAD,
                                      INTERVAL = var_ST.DT$INTERVAL),
                            mean)
var_ST.DT.sd <- aggregate(var_ST.DT$VAR,
                          by = list(WMLOAD = var_ST.DT$WMLOAD,
                                    INTERVAL = var_ST.DT$INTERVAL),
                          sd)
var_ST.DT.length <- aggregate(var_ST.DT$VAR,
                              by = list(WMLOAD = var_ST.DT$WMLOAD,
                                     INTERVAL = var_ST.DT$INTERVAL),
                              length)
names(var_ST.DT.mean)[names(var_ST.DT.mean) == "x"] <- "MEAN"
var_ST.DT.mean$SD <- var_ST.DT.sd$x
var_ST.DT.mean$N <- var_ST.DT.length$x
var_ST.DT.mean$SEM <- var_ST.DT.mean$SD / sqrt(var_ST.DT.mean$N)
```
## Figure
```{r}
f7 <- ggplot(data = var_ST.DT.mean,
             aes(x = WMLOAD,
                 y = MEAN,
                 group = INTERVAL,
                 fill = interaction(INTERVAL, WMLOAD))) +
  labs(x = "Task", y = "Subjective duration variance (s)") +
  scale_y_continuous(breaks = seq(from = 0, to = 450, by = 50),
                     limits = c(0, 450)) +
  scale_x_discrete(labels = c("Single", "Dual")) +
  theme_classic() +
  theme(legend.title = element_text(face = "bold", size = 18),
        legend.text = element_text(size = 15),
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        strip.background = element_blank(),
        strip.text = element_text(size = 20, face = "bold"),
        panel.spacing = unit(2, "lines")) +
  scale_fill_manual(values = cbPaletteBar, name = "Duration",
  labels = c("30s", "60s", "90s", "30s", "60s", "90s")) +
  geom_bar(stat = "identity", width = .8, position = position_dodge()) +
  geom_errorbar(aes(ymin = MEAN - SEM, ymax = MEAN + SEM),
  colour = "black",
  width = .1,
  show.legend = FALSE,
  position = position_dodge(.8))

# Save image
ggsave(f7,
       file = "D:/M1_thesis/analysis/f7.svg",
       dpi = 700)
```
<br><br>


# ST vs DT | CV (Figure 2d)
***
```{r}
# == Pre-compute descriptive stats =============================================
# ==============================================================================
clean_ST.DT_cv <- aggregate(merged_ST.DT_sel$ESTIMATE,
                            by = list(SUBJ = merged_ST.DT_sel$SUBJ_ID,
                                      WMLOAD = merged_ST.DT_sel$WMLOAD,
                                      INTERVAL = merged_ST.DT_sel$INTERVAL),
                            mean)

clean_ST.DT_cv.sd <- aggregate(merged_ST.DT_sel$ESTIMATE,
                               by = list(SUBJ = merged_ST.DT_sel$SUBJ_ID,
                                         WMLOAD = merged_ST.DT_sel$WMLOAD,
                                         INTERVAL = merged_ST.DT_sel$INTERVAL),
                               sd)

clean_ST.DT_cv.length <- aggregate(merged_ST.DT_sel$ESTIMATE,
                                   by = list(SUBJ = merged_ST.DT_sel$SUBJ_ID,
                                             WMLOAD = merged_ST.DT_sel$WMLOAD,
                                             INTERVAL = merged_ST.DT_sel$INTERVAL),
                                   length)

names(clean_ST.DT_cv)[names(clean_ST.DT_cv) == "x"] <- "MEAN"
clean_ST.DT_cv$SD <- clean_ST.DT_cv.sd$x
clean_ST.DT_cv$N <- clean_ST.DT_cv.length$x
clean_ST.DT_cv$CV <- clean_ST.DT_cv$SD / clean_ST.DT_cv$MEAN
clean_ST.DT_cv <- clean_ST.DT_cv[complete.cases(clean_ST.DT_cv[, 7]),]

# == Averaged CV ===============================================================
# ==============================================================================
clean_ST.DT_cv_avg <- aggregate(clean_ST.DT_cv$CV,
                                by = list(WMLOAD = clean_ST.DT_cv$WMLOAD,
                                          INTERVAL = clean_ST.DT_cv$INTERVAL),
                                mean)

clean_ST.DT_cv_avg.sd <- aggregate(clean_ST.DT_cv$CV,
                                   by = list(WMLOAD = clean_ST.DT_cv$WMLOAD,
                                             INTERVAL = clean_ST.DT_cv$INTERVAL),
                                   sd)

clean_ST.DT_cv_avg.length <- aggregate(clean_ST.DT_cv$CV,
                                       by = list(WMLOAD = clean_ST.DT_cv$WMLOAD,
                                                 INTERVAL = clean_ST.DT_cv$INTERVAL),
                                       length)

names(clean_ST.DT_cv_avg)[names(clean_ST.DT_cv_avg) == "x"] <- "MEAN"
clean_ST.DT_cv_avg$SD <- clean_ST.DT_cv_avg.sd$x
clean_ST.DT_cv_avg$N <- clean_ST.DT_cv_avg.length$x
clean_ST.DT_cv_avg$SEM <- clean_ST.DT_cv_avg$SD / sqrt(clean_ST.DT_cv_avg$N)
```
## Figure
```{r}
f8 <- ggplot(data = clean_ST.DT_cv_avg,
             aes(x = INTERVAL, y = MEAN, group = WMLOAD, colour = WMLOAD)) +
  labs(x = "Objective duration (s)", y = "CV") +
  scale_y_continuous(breaks = seq(from = 0.1, to = .3, by = .05),
                     limits = c(0.1, .3)) +
  theme_classic() +
  theme(legend.title = element_blank(),
        legend.position = c(.2, .1),
        legend.text = element_text(size = 15),
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        strip.background = element_blank(),
        strip.text = element_text(size = 20, face = "bold"),
        panel.spacing = unit(2, "lines")) +
  geom_errorbar(aes(ymin = MEAN - SEM, ymax = MEAN + SEM),
                colour = "black",
                width = .05,
                show.legend = FALSE) +
  geom_point(size = 4) +
  geom_line(aes(group = WMLOAD), 
            size = 2,
            show.legend = FALSE) +
  scale_fill_manual(values = cbPalette2,
                    labels = c("Single task", "Dual task")) +
  scale_colour_manual(values = cbPalette2,
                      labels = c("Single task", "Dual task"))

# Save image
ggsave(f8,
       file = "D:/M1_thesis/analysis/f8.svg",
       dpi = 700)
```
<br><br>


# ST vs DT[n-back] (merged Fdbck/NoFdbck) | DEVIATED DURATION ESTIMATION (Figure 3a)
***
```{r}
# == Pre-compute descriptive stats =============================================
# ==============================================================================
clean_ST.DT.devT <- aggregate(merged_ST.DT$Norm_Est,
                              by = list(WMLOAD = merged_ST.DT$WMLOAD,
                                        INTERVAL = merged_ST.DT$INTERVAL), 
                              mean)
clean_ST.DT.devT.sd <- aggregate(merged_ST.DT$Norm_Est,
                                 by = list(WMLOAD = merged_ST.DT$WMLOAD,
                                        INTERVAL = merged_ST.DT$INTERVAL), 
                                 sd)
clean_ST.DT.devT.length <- aggregate(merged_ST.DT$Norm_Est,
                                     by = list(WMLOAD = merged_ST.DT$WMLOAD,
                                               INTERVAL = merged_ST.DT$INTERVAL), 
                                     length)

names(clean_ST.DT.devT)[names(clean_ST.DT.devT) == "x"] <- "MEAN"
clean_ST.DT.devT$SD <- clean_ST.DT.devT.sd$x
clean_ST.DT.devT$N <- clean_ST.DT.devT.length$x
clean_ST.DT.devT$SEM <- clean_ST.DT.devT$SD / sqrt(clean_ST.DT.devT$N)
```
## Figure
```{r}
pd <- position_dodge(0.3)
merged_fig <- ggplot(data = clean_ST.DT.devT,
                     aes(x = WMLOAD,
                         y = MEAN,
                         group = INTERVAL,
                         colour = interaction(INTERVAL, WMLOAD))) +
  geom_hline(aes(yintercept = 0), 
             colour = 'black', 
             size = .5, 
             linetype = "dashed") +
  geom_vline(aes(xintercept = 2), 
             colour = 'black', 
             size = .5) +
  geom_errorbar(aes(ymin = MEAN - SEM, ymax = MEAN + SEM), 
                width = .1, 
                position = pd, 
                show.legend = FALSE) + 
  geom_point(size = 5, 
             position = pd) + 
  labs(x = "Working Memory load", y = "Subjective duration deviation (s)") +
  scale_x_discrete(limits = c("ST", "", "0", "1", "2", "3"), 
                   labels = c("Empty\ninterval", "", "0", "1", "2", "3")) + 
  coord_fixed(ratio = .2) + 
  guides(size = FALSE) + 
  scale_y_continuous(breaks = seq(from = -25, to = 25, by = 5),
                     limits = c(-25, 25)) + 
  theme_classic() +
  annotate("text", x = 1, y = 23, label = 'bold("Single\ntask")',
           colour = "black", parse = TRUE, size = 5) + 
  annotate("text", x = 4.5, y = 23, label = 'bold("Dual\ntask")',
           colour = "black", parse = TRUE, size = 5) +
  geom_line(data = subset(clean_ST.DT.devT, WMLOAD != "ST"), 
            aes(colour = INTERVAL), 
            size = 1.5, 
            show.legend = FALSE,
            position = pd) + 
  theme(legend.title = element_text(face = "bold", size = 18),
        legend.text = element_text(size = 15), 
        axis.text = element_text(size = 18),
        axis.title = element_text(size = 18),
        strip.background = element_blank(),
        strip.text = element_text(size = 20, face = "bold"),
        panel.spacing = unit(2, "lines")) +
  scale_colour_manual(values = cbPaletteCTRL_DT,
                      name = "Duration",
                      labels = c("30s", "60s", "90s", "30s", "60s", "90s"),
                      breaks = c("30.ST", "60.ST", "90.ST", "30", "60", "90"))

legend_wm.time <- get_legend(merged_fig)

blank_img_wm.time <- ggplot() +
  geom_blank(aes(.5, 1)) +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_blank(), 
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_blank()) +
  xlim(0, .5) +
  ylim(-20, 25) +
  annotation_custom(grob = legend_wm.time,
                    xmin = .03,
                    ymin = 3,
                    xmax = .05,
                    ymax = 3) +
  annotation_custom(grob = textGrob("Overestimation",
                                    rot = 90, 
                    gp = gpar(fontsize = 15)),
                    xmin = .18,
                    xmax = .18,
                    ymin = 14,
                    ymax = 14) +
  annotation_custom(grob = textGrob("Underestimation",
                                    rot = 90, 
                    gp = gpar(fontsize = 15)),
                    xmin = .18,
                    xmax = .18,
                    ymin = -8,
                    ymax = -8) +
  annotation_custom(grob = segmentsGrob(arrow = arrow(type = "closed", 
                                                      ends = "last"),
                                        gp = gpar(col = "grey"),
                                        name = NULL,
                                        vp = NULL),
                    xmin = .05,
                    ymin = 10,
                    xmax = .05,
                    ymax = 18) +
  annotation_custom(grob = segmentsGrob(arrow = arrow(type = "closed",
                                                      ends = "first"),
                                        gp = gpar(col = "grey"),
                                        name = NULL,
                                        vp = NULL),
                    xmin = .05,
                    ymin = -4,
                    xmax = .05,
                    ymax = -12)

f9 <- grid.arrange(merged_fig + theme(legend.position = "none"), 
                   blank_img_wm.time, ncol = 2, nrow = 1, widths = c(1, .1))

# Save image
ggsave(f9,
       file = "D:/M1_thesis/analysis/f9.svg",
       dpi = 700)
```
<br><br>


# ST vs DT | DENSITY PLOT (Figure 3b)
***
```{r}
# == Pre-compute descriptive stats =============================================
# ==============================================================================
merged_ST.DT_avg <- aggregate(merged_ST.DT$ESTIMATE,
                              by = list(SUBJ = merged_ST.DT$SUBJ_ID,
                                        WMLOAD = merged_ST.DT$WMLOAD,
                                        INTERVAL = merged_ST.DT$INTERVAL,
                                        COND = merged_ST.DT$COND),
                              mean)
names(merged_ST.DT_avg)[names(merged_ST.DT_avg) == "x"] <- "ESTIMATE"
```
## Figure
```{r}
# == ST | Density ==============================================================
# ==============================================================================
ST.den <- ggplot(subset(merged_ST.DT_avg, WMLOAD == "ST"),
                 aes(x = ESTIMATE, group = INTERVAL, fill = INTERVAL)) + 
  geom_density(aes(fill = INTERVAL), linetype = "blank", alpha = 0.5) + 
  theme_classic() +
  theme(legend.title = element_text(face = "bold", size = 18),
        legend.text = element_text(size = 15),
        legend.position = c(.32, .7),
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        axis.title.x = element_text(colour = "white"),
        axis.line.x = element_line(color = "black", size = .5),
        axis.line.y = element_line(color = "black", size = .5)) + 
  labs(y = "Density", x = "Subjective duration (s)") +
  annotate("text", x = 180, y = .05, label = 'bold("Single task")',
           size = 7, parse = TRUE) +
  scale_x_continuous(limits = c(0, 180), 
                     breaks = c(0, 30, 60, 90, 120, 150, 180), 
                     labels = c("0", "30", "60", "90", "120", "150", "180")) +
  scale_y_reverse(limits = c(.09, 0),
                  breaks = c(.0, .04, .08), 
                  labels = c(".00", ".04", ".08")) +
  coord_flip() +
  scale_fill_manual(values = cbPaletteCTRL, name = "Duration",
                    labels = c("30s", "60s", "90s"))

# == DT[0-back] | Density ======================================================
# ==============================================================================
DT0back.den <- ggplot(subset(merged_ST.DT_avg, WMLOAD == "0"),
                      aes(x = ESTIMATE, group = INTERVAL, fill = INTERVAL)) + 
  geom_density(aes(fill = INTERVAL), linetype = "blank", alpha = 0.5) + 
  theme_classic() +
  theme(legend.position = "none",
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        axis.line.y = element_line(colour = "white"),
        axis.text.y = element_text(colour = "white"),
        axis.title.x = element_text(colour = "white"),
        axis.title.y = element_text(colour = "white"),
        axis.ticks.y = element_line(colour = "white"),
        axis.line.x = element_line(color = "black", size = .5)) +
  labs(y = "Density", x = "Blabla") +
  annotate("text", x = 170, y = .05, label = 'bold("Dual task\n0-back")',
           size = 7, parse = TRUE) +
  scale_x_continuous(limits = c(0, 180), 
                     breaks = c(30, 60, 90, 120, 150, 180), 
                     labels = c("30", "60", "90", "120", "150", "180")) + 
  scale_y_continuous(limits = c(0, .09),
                     breaks = c(.0, .04, .08), 
                     labels = c(".00", ".04", ".08")) +
  scale_fill_manual(values = cbPaletteDT, name = "Time interval",
                    labels = c("30s", "60s", "90s")) +
  coord_flip()

# == DT[1-back] | Density ======================================================
# ==============================================================================
DT1back.den <- ggplot(subset(merged_ST.DT_avg, WMLOAD == "1"),
                      aes(x = ESTIMATE, group = INTERVAL, fill = INTERVAL)) + 
  geom_density(aes(fill = INTERVAL), linetype = "blank", alpha = 0.5) + 
  theme_classic() +
  theme(legend.position = "none",
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        axis.line.y = element_line(colour = "white"),
        axis.text.y = element_text(colour = "white"),
        axis.title.y = element_text(colour = "white"),
        axis.ticks.y = element_line(colour = "white"),
        axis.line.x = element_line(color = "black", size = .5)) +
  labs(y = "Density", x = "Blabla") + 
  annotate("text", x = 170, y = .05, label = 'bold("Dual task\n1-back")',
           size = 7, parse = TRUE) +
  scale_x_continuous(limits = c(0, 180), 
                     breaks = c(30, 60, 90, 120, 150, 180), 
                     labels = c("30", "60", "90", "120", "150", "180")) + 
  scale_y_continuous(limits = c(0, .09),
                     breaks = c(.0, .04, .08), 
                     labels = c(".00", ".04", ".08")) +
  scale_fill_manual(values = cbPaletteDT, name = "Time interval",
                    labels = c("30s", "60s", "90s")) +
  coord_flip()

# == DT[2-back] | Density ======================================================
# ==============================================================================
DT2back.den <- ggplot(subset(merged_ST.DT_avg, WMLOAD == "2"),
                      aes(x = ESTIMATE, group = INTERVAL, fill = INTERVAL)) + 
  geom_density(aes(fill = INTERVAL), linetype = "blank", alpha = 0.5) + 
  theme_classic() +
  theme(legend.position = "none",
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        axis.line.y = element_line(colour = "white"),
        axis.text.y = element_text(colour = "white"),
        axis.title.x = element_text(colour = "white"),
        axis.title.y = element_text(colour = "white"),
        axis.ticks.y = element_line(colour = "white"),
        axis.line.x = element_line(color = "black", size = .5)) +
  labs(y = "Density", x = "Blabla") + 
  annotate("text", x = 170, y = .05, label = 'bold("Dual task\n2-back")',
           size = 7, parse = TRUE) +
  scale_x_continuous(limits = c(0, 180), 
                     breaks = c(30, 60, 90, 120, 150, 180), 
                     labels = c("30", "60", "90", "120", "150", "180")) + 
  scale_y_continuous(limits = c(0, .09),
                     breaks = c(.0, .04, .08), 
                     labels = c(".00", ".04", ".08")) +
  scale_fill_manual(values = cbPaletteDT, name = "Time interval",
                    labels = c("30s", "60s", "90s")) +
  coord_flip()

# == DT[3-back] | Density ======================================================
# ==============================================================================
DT3back.den <- ggplot(subset(merged_ST.DT_avg, WMLOAD == "3"),
                      aes(x = ESTIMATE, group = INTERVAL, fill = INTERVAL)) + 
  geom_density(aes(fill = INTERVAL), linetype = "blank", alpha = 0.5) + 
  theme_classic() +
  theme(legend.title = element_text(face = "bold", size = 18),
        legend.text = element_text(size = 15),
        legend.position = c(.75, .7),
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        axis.line.y = element_line(colour = "white"),
        axis.text.y = element_text(colour = "white"),
        axis.title.x = element_text(colour = "white"),
        axis.title.y = element_text(colour = "white"),
        axis.ticks.y = element_line(colour = "white"),
        axis.line.x = element_line(color = "black", size = .5)) +
  labs(y = "Density", x = "Blabla") + 
  annotate("text", x = 170, y = .05, label = 'bold("Dual task\n3-back")',
           size = 7, parse = TRUE) +
  scale_x_continuous(limits = c(0, 180), 
                     breaks = c(30, 60, 90, 120, 150, 180), 
                     labels = c("30", "60", "90", "120", "150", "180")) + 
  scale_y_continuous(limits = c(0, .09),
                     breaks = c(.0, .04, .08), 
                     labels = c(".00", ".03", ".08")) +
  scale_fill_manual(values = cbPaletteDT, name = "Duration",
                    labels = c("30s", "60s", "90s")) +
  coord_flip()


# == Joint figure ST + DT ======================================================
# ==============================================================================
f10 <- grid.arrange(ST.den, DT0back.den, DT1back.den, DT2back.den, DT3back.den,
                   ncol = 5, nrow = 1, widths = c(1, 1, 1, 1, 1))

# Save image
ggsave(f10,
       file = "D:/M1_thesis/analysis/f10.svg",
       dpi = 700)
```
<br><br>


# DT[n-back] | CV (Figure 3c)
***
```{r}
# == Pre-compute descriptive stats =============================================
# ==============================================================================
clean_DTnback_cv <- aggregate(pre_merged_DT$ESTIMATE,
                              by = list(SUBJ = pre_merged_DT$SUBJ_ID,
                                        WMLOAD = pre_merged_DT$WMLOAD,
                                        INTERVAL = pre_merged_DT$INTERVAL),
                              mean)

clean_DTnback_cv.sd <- aggregate(pre_merged_DT$ESTIMATE,
                                 by = list(SUBJ = pre_merged_DT$SUBJ_ID,
                                         WMLOAD = pre_merged_DT$WMLOAD,
                                         INTERVAL = pre_merged_DT$INTERVAL),
                                 sd)

clean_DTnback_cv.length <- aggregate(pre_merged_DT$ESTIMATE,
                                     by = list(SUBJ = pre_merged_DT$SUBJ_ID,
                                             WMLOAD = pre_merged_DT$WMLOAD,
                                             INTERVAL = pre_merged_DT$INTERVAL),
                                     length)

names(clean_DTnback_cv)[names(clean_DTnback_cv) == "x"] <- "MEAN"
clean_DTnback_cv$SD <- clean_DTnback_cv.sd$x
clean_DTnback_cv$N <- clean_DTnback_cv.length$x
clean_DTnback_cv$CV <- clean_DTnback_cv$SD / clean_DTnback_cv$MEAN
clean_DTnback_cv <- clean_DTnback_cv[complete.cases(clean_DTnback_cv[, 7]),]

# == Averaged CV ===============================================================
# ==============================================================================
clean_DTnback_cv_avg <- aggregate(clean_DTnback_cv$CV,
                                  by = list(WMLOAD = clean_DTnback_cv$WMLOAD),
                                  mean)

clean_DTnback_cv_avg.sd <- aggregate(clean_DTnback_cv$CV,
                                     by = list(WMLOAD = clean_DTnback_cv$WMLOAD),
                                     sd)

clean_DTnback_cv_avg.length <- aggregate(clean_DTnback_cv$CV,
                                         by = list(WMLOAD = clean_DTnback_cv$WMLOAD),
                                         length)

names(clean_DTnback_cv_avg)[names(clean_DTnback_cv_avg) == "x"] <- "MEAN"
clean_DTnback_cv_avg$SD <- clean_DTnback_cv_avg.sd$x
clean_DTnback_cv_avg$N <- clean_DTnback_cv_avg.length$x
clean_DTnback_cv_avg$SEM <- clean_DTnback_cv_avg$SD / sqrt(clean_DTnback_cv_avg$N)
```
## Figure
```{r}
f11 <- ggplot(data = clean_DTnback_cv_avg, aes(x = WMLOAD, y = MEAN)) +
  labs(x = "Working Memory load", y = "CV") +
  scale_y_continuous(breaks = seq(from = 0.16, to = .28, by = .02),
                     limits = c(0.16, .28)) +
  theme_classic() +
  geom_line(aes(group = WMLOAD),
            size = 2,
            show.legend = FALSE) +
  theme(axis.title = element_text(size = 18),
  axis.text = element_text(size = 18),
  strip.background = element_blank(),
  strip.text = element_text(size = 20, face = "bold"),
  panel.spacing = unit(2, "lines")) +
  geom_errorbar(aes(ymin = MEAN - SEM, ymax = MEAN + SEM),
                colour = "black",
                width = .05,
                show.legend = FALSE) +
  geom_point(size = 2)

# Save image
ggsave(f11,
       file = "D:/M1_thesis/analysis/f11.svg",
       dpi = 700)
```
<br><br>


# ST vs DT[0-back] | SUBJECTIVE DURATION DEVIATION | separate Fdbck/NoFdbck (Supplementary figure 1b)
***
```{r}
# == Pre-compute descriptive stats =============================================
# ==============================================================================
ST.0back_facet_devT_avg <- aggregate(ST.0back$Norm_Est,
                                     by = list(WMLOAD = ST.0back$WMLOAD,
                                               INTERVAL = ST.0back$INTERVAL,
                                               COND = ST.0back$COND), 
                                     mean)
ST.0back_facet_devT_avg.sd <- aggregate(ST.0back$Norm_Est,
                                        by = list(WMLOAD = ST.0back$WMLOAD,
                                                  INTERVAL = ST.0back$INTERVAL,
                                                  COND = ST.0back$COND), 
                                        sd)
ST.0back_facet_devT_avg.length <- aggregate(ST.0back$Norm_Est,
                                            by = list(WMLOAD = ST.0back$WMLOAD,
                                                      INTERVAL = ST.0back$INTERVAL,
                                                      COND = ST.0back$COND), 
                                            length)

names(ST.0back_facet_devT_avg)[names(ST.0back_facet_devT_avg) == "x"] <- "MEAN"
ST.0back_facet_devT_avg$SD <- ST.0back_facet_devT_avg.sd$x
ST.0back_facet_devT_avg$N <- ST.0back_facet_devT_avg.length$x
ST.0back_facet_devT_avg$SEM <- ST.0back_facet_devT_avg$SD / sqrt(ST.0back_facet_devT_avg$N)
```
## Figure
```{r}
pd <- position_dodge(0.2)
f12 <- ggplot(data = ST.0back_facet_devT_avg,
              aes(x = INTERVAL, y = MEAN, group = WMLOAD, colour = WMLOAD)) +
  labs(x = "Objective duration (s)", y = "Subjective duration deviation (s)") +
  scale_y_continuous(breaks = seq(from = -14, to = 14, by = 2),
                     limits = c(-14, 14)) +
  geom_hline(aes(yintercept = 0), 
             colour = 'black', 
             size = .5, 
             linetype = "dashed") +
  theme_classic() +
  theme(legend.title = element_blank(),
  legend.text = element_text(size = 15),
  legend.position = c(.2, .1),
  axis.title = element_text(size = 18),
  axis.text = element_text(size = 18),
  strip.background = element_blank(),
  strip.text = element_text(size = 20, face = "bold"),
  panel.spacing = unit(2, "lines")) +
  geom_errorbar(aes(ymin = MEAN - SEM, ymax = MEAN + SEM),
                width = .05,
                show.legend = FALSE,
                position = pd) +
  geom_point(size = 4,
             position = pd) +
  geom_line(aes(group = WMLOAD), 
            size = 2,
            show.legend = FALSE,
            position = pd) +
  scale_fill_manual(values = cbPaletteST0back,
                    labels = c("Single task",
                               "Dual task: 0-back")) +
  scale_colour_manual(values = cbPaletteST0back,
                      labels = c("Single task",
                                 "Dual task: 0-back")) +
  facet_grid(~COND,
             labeller = labeller(COND = c(NoFdbck = 'NO FEEDBACK',
                                          Fdbck = 'FEEDBACK')))
# Save image
ggsave(f12,
       file = "D:/M1_thesis/analysis/f12.svg",
       dpi = 700)
```
<br><br>


# ST vs DT[n-back] | SUBJECTIVE DURATION DEVIATION | separate Fdbck/NoFdbck (Supplementary figure 3)
***
```{r}
# == Pre-compute descriptive stats =============================================
# ==============================================================================
clean_ST.DT_facet_devT <- aggregate(merged_ST.DT$Norm_Est,
                                    by = list(WMLOAD = merged_ST.DT$WMLOAD,
                                              INTERVAL = merged_ST.DT$INTERVAL,
                                              COND = merged_ST.DT$COND), 
                                    mean)
clean_ST.DT_facet_devT.sd <- aggregate(merged_ST.DT$Norm_Est,
                                       by = list(WMLOAD = merged_ST.DT$WMLOAD,
                                                 INTERVAL = merged_ST.DT$INTERVAL,
                                                 COND = merged_ST.DT$COND), 
                                       sd)
clean_ST.DT_facet_devT.length <- aggregate(merged_ST.DT$Norm_Est,
                                           by = list(WMLOAD = merged_ST.DT$WMLOAD,
                                                     INTERVAL = merged_ST.DT$INTERVAL,
                                                     COND = merged_ST.DT$COND), 
                                           length)

names(clean_ST.DT_facet_devT)[names(clean_ST.DT_facet_devT) == "x"] <- "MEAN"
clean_ST.DT_facet_devT$SD <- clean_ST.DT_facet_devT.sd$x
clean_ST.DT_facet_devT$N <- clean_ST.DT_facet_devT.length$x
clean_ST.DT_facet_devT$SEM <- clean_ST.DT_facet_devT$SD / sqrt(clean_ST.DT_facet_devT$N)
```
## Figure
```{r}
facet_fig_col_code <- ggplot(data = clean_ST.DT_facet_devT,
                             aes(x = WMLOAD,
                                 y = MEAN,
                                 group = INTERVAL,
                                 colour = interaction(INTERVAL, WMLOAD))) +
  geom_hline(aes(yintercept = 0), 
             colour = 'black', 
             size = .5, 
             linetype = "dashed") +
  geom_vline(aes(xintercept = 2), 
             colour = 'black', 
             size = .5) +
  geom_errorbar(aes(ymin = MEAN - SEM, ymax = MEAN + SEM), 
                width = .1, 
                position = pd, 
                show.legend = FALSE) + 
  geom_point(size = 5, 
             position = pd) + 
  labs(x = "Working Memory load", y = "Subjective duration deviation (s)") +
  scale_x_discrete(limits = c("ST", "", "0", "1", "2", "3"), 
                   labels = c("Empty\ninterval", "", "0", "1", "2", "3")) + 
  coord_fixed(ratio = .2) + 
  guides(size = FALSE) + 
  scale_y_continuous(breaks = seq(from = -25, to = 25, by = 5),
                     limits = c(-25, 25)) + 
  theme_classic() + 
  geom_line(data = subset(summary.pr.ctrl.2_avg, WMLOAD != "ST"), 
            aes(colour = INTERVAL), 
            size = 1.5, 
            show.legend = FALSE,
            position = pd) + 
  theme(legend.title = element_text(face = "bold", size = 18),
        legend.text = element_text(size = 15), 
        axis.text = element_text(size = 18),
        axis.title = element_text(size = 18),
        strip.background = element_blank(),
        strip.text = element_text(size = 20, face = "bold"),
        panel.spacing = unit(2, "lines")) +
  scale_colour_manual(values = cbPaletteCTRL_DT,
                      name = "Duration",
                      labels = c("30s Single task",
                                 "60s Single task",
                                 "90s Single task",
                                 "30s Dual task",
                                 "60s Dual task",
                                 "90s Dual task"),
                      breaks = c("30.ST", "60.ST", "90.ST", "30", "60", "90")) +
  facet_grid(~COND,
             labeller = labeller(COND = c(NoFdbck = 'NO FEEDBACK',
                                          Fdbck = 'FEEDBACK')))
#  annotate("text", x= 1, y= 23, label= 'bold("Single\ntask")', colour= "black", parse=TRUE, size=5) + 
#  annotate("text", x= 4.5, y= 23, label= 'bold("Dual\ntask")', colour= "black", parse=TRUE, size=5) +

legend_wm.time <- get_legend(facet_fig_col_code)

blank_img_wm.time <- ggplot() +
  geom_blank(aes(.5, 1)) +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_blank(), 
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_blank()) +
  xlim(0, .5) +
  ylim(-20, 25) +
  annotation_custom(grob = legend_wm.time,
                    xmin = .03,
                    ymin = 3,
                    xmax = .05,
                    ymax = 3) +
  annotation_custom(grob = textGrob("Overestimation",
                                    rot = 90, 
                    gp = gpar(fontsize = 15)),
                    xmin = .18,
                    xmax = .18,
                    ymin = 14,
                    ymax = 14) +
  annotation_custom(grob = textGrob("Underestimation",
                                    rot = 90, 
                    gp = gpar(fontsize = 15)),
                    xmin = .18,
                    xmax = .18,
                    ymin = -8,
                    ymax = -8) +
  annotation_custom(grob = segmentsGrob(arrow = arrow(type = "closed", 
                                                    ends = "last"),
                                        gp = gpar(col = "grey"),
                                        name = NULL,
                                        vp = NULL),
                    xmin = .05,
                    ymin = 10,
                    xmax = .05,
                    ymax = 18) +
  annotation_custom(grob = segmentsGrob(arrow = arrow(type = "closed",
                                                      ends = "first"),
                                        gp = gpar(col = "grey"),
                                        name = NULL,
                                        vp = NULL),
                    xmin = .05,
                    ymin = -4,
                    xmax = .05,
                    ymax = -12)

f13 <- grid.arrange(facet_fig_col_code + theme(legend.position = "none"), 
                    blank_img_wm.time, ncol = 2, nrow = 1, widths = c(1, .1))

# Save image
ggsave(f12,
       file = "D:/M1_thesis/analysis/f13.svg",
       dpi = 700)
```
<br><br>


# MODEL TESTING | SUBJECTIVE DURATION DEVIATION | ST vs DT[0-back] (Supplementary figure 1a)
```{r}
ST.0back <- subset(merged_ST.DT, WMLOAD == "ST" | WMLOAD == "0")

# == ST differences across Duration ==
zz <- subset(ST.0back, WMLOAD == "ST")
STdiff_model_0 <- lmer(Norm_Est ~ 1 + (1 | SUBJ_ID),
                       data = zz,
                       REML = FALSE)
STdiff_model_1 <- lmer(Norm_Est ~ INTERVAL + (1 | SUBJ_ID),
                       data = zz,
                       REML = FALSE)

lrtest(STdiff_model_0, STdiff_model_1)
AIC(STdiff_model_0, STdiff_model_1)

summary(STdiff_model_1)
lsmeans(STdiff_model_1, pairwise ~ INTERVAL)

# == DT:0-back differences across Duration ==
ww <- subset(ST.0back, WMLOAD == "0")
DT.0back_diff_model_0 <- lmer(Norm_Est ~ 1 + (1 | SUBJ_ID),
                              data = ww,
                              REML = FALSE)
DT.0back_diff_model_1 <- lmer(Norm_Est ~ INTERVAL + (1 | SUBJ_ID),
                              data = ww,
                              REML = FALSE)

lrtest(DT.0back_diff_model_0, DT.0back_diff_model_1)
AIC(DT.0back_diff_model_0, DT.0back_diff_model_1)

summary(STdiff_model_1)
lsmeans(DT.0back_diff_model_1, pairwise ~ INTERVAL)

# == ST vs DT[0-back] ==========================================================
# == Deviated subjective duration estimation ===================================
STvs0back_model_0 <- lmer(Norm_Est ~ 1 + (1 | SUBJ_ID),
                          data = ST.0back,
                          REML = FALSE)
STvs0back_model_1 <- lmer(Norm_Est ~ WMLOAD + (1 | SUBJ_ID),
                          data = ST.0back,
                          REML = FALSE)

lrtest(STvs0back_model_0, STvs0back_model_1)
AIC(STvs0back_model_0, STvs0back_model_1)

STvs0back_model_2 <- lmer(Norm_Est ~ WMLOAD + INTERVAL + (1 | SUBJ_ID),
                          data = ST.0back,
                          REML = FALSE)

lrtest(STvs0back_model_1, STvs0back_model_2)
AIC(STvs0back_model_1, STvs0back_model_2)

STvs0back_model_3 <- lmer(Norm_Est ~ WMLOAD * INTERVAL + (1 | SUBJ_ID),
                          data = ST.0back,
                          REML = FALSE)

lrtest(STvs0back_model_2, STvs0back_model_3)
AIC(STvs0back_model_2, STvs0back_model_3)

summary(STvs0back_model_3)


v <- visreg(STvs0back_model_3, "INTERVAL", by = "WMLOAD", overlay = TRUE)
plot(v,
     main = "Regression model Single task vs Dual task: 0-back",
     xlab = "Objective duration (s)",
     ylab = "Subjective duration deviation (s)",
     ylim = c(-80, 80),
     yaxt = "n",
     overlay = TRUE,
     points.par = list(col = cbPaletteST0back),
     line.par = list(col = cbPaletteST0back, lwd = 5),
     legend = FALSE)
axis(2, at = seq(-80, 80, 10), las = 2)
abline(h = 0, lty = 2, lwd = 3)
legend("bottomleft", legend = c("Single task", "Dual task"),
       fill = cbPaletteST0back, border = cbPaletteST0back, bty = "n")

# ----- Pairwise comparisons ------------------------
# -- Main effect of Task ----------------------------
lsmeans(STvs0back_model_3, pairwise ~ WMLOAD | INTERVAL)

# -- Main effect of Interval ------------------------
lsmeans(STvs0back_model_3, pairwise ~ INTERVAL | WMLOAD)
    
# -- Main effect of Interaction WM load / Feedback --
contrast(lsmeans(STvs0back_model_3, pairwise ~ WMLOAD | INTERVAL), 
         interaction = "pairwise")


# == ST vs DT[0-back] (Feedback vs No Feedback) ================================
# == Deviated subjective duration estimation ===================================
STvs0back_model_facet_0 <- lmer(Norm_Est ~ 1  + (1 | SUBJ_ID),
                                data = subset(ST.0back, COND == "NoFdbck"),
                                REML = FALSE)
STvs0back_model_facet_1 <- lmer(Norm_Est ~ 1  + WMLOAD + (1 | SUBJ_ID),
                                data = subset(ST.0back, COND == "NoFdbck"),
                                REML = FALSE)
STvs0back_model_facet_2 <- lmer(Norm_Est ~ WMLOAD + INTERVAL + (1 | SUBJ_ID),
                                data = subset(ST.0back, COND == "NoFdbck"),
                                REML = FALSE)
STvs0back_model_facet_3 <- lmer(Norm_Est ~ WMLOAD * INTERVAL + (1 | SUBJ_ID),
                                data = subset(ST.0back, COND == "NoFdbck"),
                                REML = FALSE)


STvs0back_model_1 <- lmer(Norm_Est ~ WMLOAD  + (1 | SUBJ_ID),
                          data = subset(STvs0back_data, COND == "Fdbck"),
                          REML = FALSE)

lrtest(STvs0back_model_facet_0, STvs0back_model_facet_1)
AIC(STvs0back_model_facet_0, STvs0back_model_facet_1)

STvs0back_model_2 <- lmer(Norm_Est ~ WMLOAD + INTERVAL + (1 | SUBJ_ID),
                          data = subset(STvs0back_data, COND == "Fdbck"),
                          REML = FALSE)

lrtest(STvs0back_model_1, STvs0back_model_2)
AIC(STvs0back_model_1, STvs0back_model_2)

STvs0back_model_3 <- lmer(Norm_Est ~ WMLOAD * INTERVAL + (1 | SUBJ_ID),
                          data = subset(STvs0back_data, COND == "Fdbck"),
                          REML = FALSE)

lrtest(STvs0back_model_2, STvs0back_model_3)
AIC(STvs0back_model_2, STvs0back_model_3)

lsmeans(STvs0back_model_3, pairwise ~ INTERVAL | WMLOAD)
```
<br><br>


# MODEL TESTING | CV | ST vs DT[0-back]
***
```{r}
STvs0back.CV_model_0 <- lmer(CV ~ 1 + (1 | SUBJ),
                             data = clean_0back_cv_avg, REML = FALSE)
STvs0back.CV_model_1 <- lmer(CV ~ WMLOAD + (1 | SUBJ),
                             data = clean_0back_cv_avg, REML = FALSE)
STvs0back.CV_model_1 <- lmer(CV ~ INTERVAL + (1 | SUBJ),
                             data = clean_0back_cv_avg, REML = FALSE)

lrtest(STvs0back.CV_model_0, STvs0back.CV_model_1)
AIC(STvs0back.CV_model_0, STvs0back.CV_model_1)
```
<br><br>


# MODEL TESTING | SUBJECTIVE DURATION DEVIATION | ST vs DT (Supplementary figure 2)
***
```{r}
STvsDT_model_0 <- lmer(Norm_Est ~ 1 + (1 | SUBJ_ID),
                       data = merged_ST.DT_sel, REML = FALSE)
STvsDT_model_1 <- lmer(Norm_Est ~ WMLOAD + (1 | SUBJ_ID),
                       data = merged_ST.DT_sel, REML = FALSE)

lrtest(STvsDT_model_0, STvsDT_model_1)
AIC(STvsDT_model_0, STvsDT_model_1)

STvsDT_model_2 <- lmer(Norm_Est ~ WMLOAD + INTERVAL + (1 | SUBJ_ID),
                       data = merged_ST.DT_sel, REML = FALSE)

lrtest(STvsDT_model_1, STvsDT_model_2)
AIC(STvsDT_model_1, STvsDT_model_2)

STvsDT_model_3 <- lmer(Norm_Est ~ WMLOAD * INTERVAL + (1 | SUBJ_ID),
                       data = merged_ST.DT_sel, REML = FALSE)

lrtest(STvsDT_model_2, STvsDT_model_3)
AIC(STvsDT_model_2, STvsDT_model_3)


# ----- Pairwise comparisons ----------------------
# -- Main effect of WM load --
lsmeans(STvsDT_model_3, pairwise ~ WMLOAD | INTERVAL)

# -- Main effect of Feedback --
lsmeans(STvsDT_model_3, pairwise ~ INTERVAL | WMLOAD)
    
# -- Main effect of Interaction WM load / Feedback --
contrast(lsmeans(STvsDT_model_3, pairwise ~ WMLOAD | INTERVAL),
         interaction = "pairwise")


v2 <- visreg(STvsDT_model_3, "INTERVAL", by = "WMLOAD", overlay = TRUE)
plot(v2,
     main = "Regression model Single task vs Dual task",
     xlab = "Objective duration (s)",
     ylab = "Subjective duration deviation (s)",
     ylim = c(-80, 80),
     yaxt = "n",
     overlay = TRUE,
     points.par = list(col = cbPalette2),
     line.par = list(col = cbPalette2, lwd = 5),
     legend = FALSE)
axis(2, at = seq(-80, 80, 10), las = 2)
abline(h = 0, lty = 2, lwd = 3)
legend("bottomleft", legend = c("Single task", "Dual task"),
       fill = cbPalette2, border = cbPalette2, bty = "n")
```
<br><br>


# MODEL TESTING | SUBJECTIVE DURATION VARIANCE | ST vs DT
***
```{r}
var_model_0 <- lmer(VAR ~ 1 + (1 | SUBJ), data = var_ST.DT)
var_model_1 <- lmer(VAR ~ INTERVAL + (1 | SUBJ), data = var_ST.DT)

lrtest(var_model_0, var_model_1)
AIC(var_model_0, var_model_1)

var_model_2 <- lmer(VAR ~ INTERVAL + WMLOAD + (1 | SUBJ), data = var_ST.DT)

lrtest(var_model_1, var_model_2)
AIC(var_model_1, var_model_2)

var_model_3 <- lmer(VAR ~ INTERVAL * WMLOAD + (1 | SUBJ), data = var_ST.DT)

lrtest(var_model_2, var_model_3)
AIC(var_model_2, var_model_3)

# ----- Pairwise comparisons ----------------------
# -- Main effect of Duration --
lsmeans(var_model_3, pairwise ~ INTERVAL | WMLOAD)
lsmeans(var_model_3, revpairwise ~ INTERVAL | WMLOAD)

# -- Main effect of WM load --
lsmeans(var_model_3, pairwise ~ WMLOAD | INTERVAL)
```
<br><br>


# MODEL TESTING | CV | ST vs DT
***
```{r}
cv_model_0 <- lmer(CV ~ 1 + (1 | SUBJ),
                   data = clean_ST.DT_cv, REML = FALSE)
cv_model_1 <- lmer(CV ~ WMLOAD + (1 | SUBJ),
                   data = clean_ST.DT_cv, REML = FALSE)

lrtest(cv_model_0, cv_model_1)
AIC(cv_model_0, cv_model_1)

cv_model_2 <- lmer(CV ~ WMLOAD + INTERVAL + (1 | SUBJ),
                   data = clean_ST.DT_cv, REML = FALSE)

lrtest(cv_model_1, cv_model_2)
AIC(cv_model_1, cv_model_2)

cv_model_3 <- lmer(CV ~ WMLOAD * INTERVAL + (1 | SUBJ),
                   data = clean_ST.DT_cv, REML = FALSE)

lrtest(cv_model_2, cv_model_3)
AIC(cv_model_2, cv_model_3)

# ----- Pairwise comparisons ----------------------
# -- Main effect of WM load -----------------------
lsmeans(cv_model_3, pairwise ~ WMLOAD | INTERVAL)
lsmeans(cv_model_1, pairwise ~ WMLOAD)
```
<br><br>


# MODEL TESTNG | SUBJECTIVE DURATION DEVIATION | ST / DT[n-back]
***
```{r}
# == Merged groups ==
TIME_model_merged_0 <- lmer(Norm_Est ~ 1 + (1 | SUBJ_ID),
                            data = subset(merged_ST.DT, WMLOAD != "ST"),
                            REML = FALSE)
TIME_model_merged_1 <- lmer(Norm_Est ~ WMLOAD + (1 | SUBJ_ID),
                            data = subset(merged_ST.DT, WMLOAD != "ST"),
                            REML = FALSE)

lrtest(TIME_model_merged_0, TIME_model_merged_1)
AIC(TIME_model_merged_0, TIME_model_merged_1)

TIME_model_merged_2 <- lmer(Norm_Est ~ WMLOAD + INTERVAL + (1 | SUBJ_ID),
                            data = subset(merged_ST.DT, WMLOAD != "ST"),
                            REML = FALSE)

lrtest(TIME_model_merged_1, TIME_model_merged_2)
AIC(TIME_model_merged_1, TIME_model_merged_2)

TIME_model_merged_3 <- lmer(Norm_Est ~ WMLOAD * INTERVAL + (1 | SUBJ_ID),
                            data = subset(merged_ST.DT, WMLOAD != "ST"),
                            REML = FALSE)

lrtest(TIME_model_merged_2, TIME_model_merged_3)
AIC(TIME_model_merged_2, TIME_model_merged_3)

plot(fitted(TIME_model_merged_3),
     residuals(TIME_model_merged_3),
     xlab = "Fitted values",
     ylab = "Residuals")
abline(h = 0, lty = 2)
lines(smooth.spline(fitted(TIME_model_merged_3),
                    residuals(TIME_model_merged_3)),
      col = "red")

# ----- Pairwise comparisons ----------------------
# -- Main effect of WM load --
lsmeans(TIME_model_merged_3, pairwise ~ WMLOAD | INTERVAL)

# -- Main effect of Feedback --
lsmeans(TIME_model_merged_3, pairwise ~ INTERVAL | WMLOAD)
    
# -- Main effect of Interaction WM load / Feedback --
contrast(lsmeans(TIME_model_merged_3, pairwise ~ WMLOAD | INTERVAL),
         interaction = "pairwise")
```
<br><br>


# MODEL TESTNG | SUBJECTIVE DURATION DEVIATION | ST / DT[n-back] | Feedback vs No Feedback
***
```{r}
# == Feedback =============
# =========================
TIME_model_fdbck_0 <- lmer(Norm_Est ~ 1 + (1 | SUBJ_ID),
                           data = subset(merged_ST.DT, WMLOAD != "ST" & COND == "Fdbck"),
                           REML = FALSE)
TIME_model_fdbck_1 <- lmer(Norm_Est ~ WMLOAD + (1 | SUBJ_ID),
                           data = subset(merged_ST.DT, WMLOAD != "ST" & COND == "Fdbck"),
                           REML = FALSE)

lrtest(TIME_model_fdbck_0, TIME_model_fdbck_1)
AIC(TIME_model_fdbck_0, TIME_model_fdbck_1)

TIME_model_fdbck_2 <- lmer(Norm_Est ~ WMLOAD + INTERVAL + (1 | SUBJ_ID),
                           data = subset(merged_ST.DT, WMLOAD != "ST" & COND == "Fdbck"),
                           REML = FALSE)

lrtest(TIME_model_fdbck_1, TIME_model_fdbck_2)
AIC(TIME_model_fdbck_1, TIME_model_fdbck_2)

TIME_model_fdbck_3 <- lmer(Norm_Est ~ WMLOAD * INTERVAL + (1 | SUBJ_ID),
                           data = subset(merged_ST.DT, WMLOAD != "ST" & COND == "Fdbck"),
                           REML = FALSE)

lrtest(TIME_model_fdbck_2, TIME_model_fdbck_3)
AIC(TIME_model_fdbck_2, TIME_model_fdbck_3)

plot(fitted(TIME_model_fdbck_3), residuals(TIME_model_fdbck_3),
     xlab = "Fitted values",
     ylab = "Residuals")
abline(h = 0, lty = 2)
lines(smooth.spline(fitted(TIME_model_fdbck_3),
                    residuals(TIME_model_fdbck_3)),
      col = "red")

# ----- Pairwise comparisons ----------------------
# -- Main effect of WM load --
lsmeans(TIME_model_fdbck_3, pairwise ~ WMLOAD | INTERVAL)

# -- Main effect of Feedback --
lsmeans(TIME_model_fdbck_3, pairwise ~ INTERVAL | WMLOAD)
    
# -- Main effect of Interaction WM load / Feedback --
contrast(lsmeans(TIME_model_fdbck_3, pairwise ~ WMLOAD | INTERVAL),
         interaction = "pairwise")


# == No Feedback =============
# ============================
TIME_model_NoFdbck_0 <- lmer(Norm_Est ~ 1 + (1 | SUBJ_ID),
                             data = subset(merged_ST.DT, WMLOAD != "ST" & COND == "NoFdbck"),
                             REML = FALSE)
TIME_model_NoFdbck_1 <- lmer(Norm_Est ~ WMLOAD + (1 | SUBJ_ID),
                             data = subset(merged_ST.DT, WMLOAD != "ST" & COND == "NoFdbck"),
                             REML = FALSE)

lrtest(TIME_model_NoFdbck_0, TIME_model_NoFdbck_1)
AIC(TIME_model_NoFdbck_0, TIME_model_NoFdbck_1)

TIME_model_NoFdbck_2 <- lmer(Norm_Est ~ WMLOAD + INTERVAL + (1 | SUBJ_ID),
                             data = subset(merged_ST.DT, WMLOAD != "ST" & COND == "NoFdbck"),
                             REML = FALSE)

lrtest(TIME_model_NoFdbck_1, TIME_model_NoFdbck_2)
AIC(TIME_model_NoFdbck_1, TIME_model_NoFdbck_2)

TIME_model_NoFdbck_3 <- lmer(Norm_Est ~ WMLOAD * INTERVAL + (1 | SUBJ_ID),
                             data = subset(merged_ST.DT, WMLOAD != "ST" & COND == "NoFdbck"),
                             REML = FALSE)

lrtest(TIME_model_NoFdbck_2, TIME_model_NoFdbck_3)
AIC(TIME_model_NoFdbck_2, TIME_model_NoFdbck_3)

plot(fitted(TIME_model_NoFdbck_3), residuals(TIME_model_NoFdbck_3),
     xlab = "Fitted values",
     ylab = "Residuals")
abline(h = 0, lty = 2)
lines(smooth.spline(fitted(TIME_model_NoFdbck_3),
                    residuals(TIME_model_NoFdbck_3)), col = "red")

# ----- Pairwise comparisons ----------------------
# -- Main effect of WM load --
lsmeans(TIME_model_NoFdbck_3, pairwise ~ WMLOAD | INTERVAL)

# -- Main effect of Feedback --
lsmeans(TIME_model_NoFdbck_3, pairwise ~ INTERVAL | WMLOAD)
    
# -- Main effect of Interaction WM load / Feedback --
contrast(lsmeans(TIME_model_NoFdbck_3, pairwise ~ WMLOAD | INTERVAL),
         interaction = "pairwise")
```
<br><br>


# MODEL TESTNG | CV | DT[n-back]
***
```{r}
cv_WMLOAD_model_0 <- lmer(CV ~ 1 + (1 | SUBJ),
                          data = clean_DTnback_cv,
                          REML = FALSE)
cv_WMLOAD_model_1 <- lmer(CV ~ WMLOAD + (1 | SUBJ),
                          data = clean_DTnback_cv,
                          REML = FALSE)

lrtest(cv_WMLOAD_model_0, cv_WMLOAD_model_1)
AIC(cv_WMLOAD_model_0, cv_WMLOAD_model_1)

cv_WMLOAD_model_2 <- lmer(CV ~ WMLOAD + INTERVAL + (1 | SUBJ),
                          data = clean_DTnback_cv,
                          REML = FALSE)

lrtest(cv_WMLOAD_model_1, cv_WMLOAD_model_2)
AIC(cv_WMLOAD_model_1, cv_WMLOAD_model_2)

summary(cv_WMLOAD_model_1)
lsmeans(cv_WMLOAD_model_1, pairwise ~ WMLOAD)
```
<br><br>