---
title: "Passage of Time"
output:
  html_document:
    df_print: paged
    toc: yes
---

<!-- # This is the Blursday database paper source code. -->
<!-- # This code was used to prepare the following article: -->
<!-- # XXX Ref. to add XXX -->
<!-- # -->
<!-- # The live application of the server can be accessed at  -->
<!-- # https://TimeSocialDistancing.shinyapps.io/Blursday/ -->
<!-- # This code is publicly available at -->
<!-- # https://github.com/dnacombo/TSDshiny -->

<!-- #     Copyright (C) 2021  Maximilien Chaumon -->
<!-- # -->
<!-- #     This program is free software: you can redistribute it and/or modify -->
<!-- #     it under the terms of the GNU General Public License as published by -->
<!-- #     the Free Software Foundation, either version 3 of the License, or -->
<!-- #     (at your option) any later version. -->
<!-- # -->
<!-- #     This program is distributed in the hope that it will be useful, -->
<!-- #     but WITHOUT ANY WARRANTY; without even the implied warranty of -->
<!-- #     MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the -->
<!-- #     GNU General Public License for more details. -->
<!-- # -->
<!-- #     You should have received a copy of the GNU General Public License -->
<!-- #     along with this program.  If not, see <http://www.gnu.org/licenses/>. -->

```{r, message=F}
source('helpers.R')
library(MaxPac)
library(effectsize)
theme_set(theme_minimal())


suppressWarnings(dir.create('PaperFigures'))

```

# Reading data

We read data from the `RetroDuration` questionnaire. Translate responses using QTranslate() (google sheet). Read response to the `initial_RetrospectiveDuration` question. Extract estimated duration since last login as `##:##:##` --\> Hours:Minutes:Seconds. Compute `ClockDuration` as the difference between current time and last login.

```{r, message=F}
# load(file.path(dirBlursday,'Demographics.RData'))
load(file.path(dirBlursday,'Daily_Login_Times.RData'))

# Extracting data:

# RetroDuration_PoT <- gimmeRdata(dirBlursday, UniqueName = 'RetroDuration') %>%
#   filter(!Country %in% c('UK','CO', 'US')) %>%
#   QTranslate() %>%
#   filter(Question_Key %in% c('Passage_of_Time')) %>%
#   mutate(Date = lubridate::date(Local_Date)) %>%
#   pivot_wider(id_cols = c('PID', 'Session','Run', 'Country', 'Local_Date'), names_from = Question_Key, values_from = Response) %>%
#   # take only the first response if there are several ones
#   group_by(PID,Session,Run,Country) %>%
#   slice(1) %>%
#   add_Demographics() %>%
#   # Using 3 AM to change day
#   mutate(Date = lubridate::as_date(Local_Date - lubridate::duration(hours = 3)),
#          Passage_of_Time = as.numeric(Passage_of_Time)) %>%
#   left_join(select(daily_login_times, PID, Session, Local_Date, Date), by = c('PID','Date'), suffix = c('','_First_Login')) %>%
#   mutate(Date = lubridate::as_date(Local_Date)) %>%
#   mutate(ClockDuration = Local_Date - Local_Date_First_Login) %>%
#   select(Country, PID, Session, Run, Local_Date, ClockDuration, Passage_of_Time,
#          Handedness, Sex, Age, Date) %>%
#   mutate(ClockDuration = lubridate::as.duration(ClockDuration)) %>%
#   ungroup() %>%
#   drop_na(Passage_of_Time, Age)
# 
# save(RetroDuration_PoT, file = file.path(dirBlursday,'RetroDuration_PoT.RData'))

load(file = file.path(dirBlursday,'RetroDuration_PoT.RData'))
```


# Outliers detection and clean up

```{r}
RetroDuration_PoT %>%
  mutate(across(c(ClockDuration, Passage_of_Time), as.numeric)) %>%
  pivot_longer(cols = c(ClockDuration,Passage_of_Time)) %>%
ggplot(aes(x = value, fill = Country)) + 
  geom_histogram(bins = 50) +
  facet_wrap(~name ,scales = 'free') +
  ggtitle('Measure distributions')
```

Distribution of `ClockDuration` is highly skewed to the left. First capping ClockDuration to decent durations, then removing 5% most extreme values.

Rationale:

-   `ClockDuration` cannot be below 60 s: no questionnaire/task can be completed under this duration, and we want at least one.
-   5% Largest/smallest `ClockDuration` is systematically discarded. This is done for each Session and Country separately.

We count these

```{r}
# capped_outliers:
Duration_max <- 18000
Duration_min <- 60
# trim_outliers:
probs <- c(.025, .975)

RetroDuration_PoT_clean <- RetroDuration_PoT %>%
  filter(!is.na(ClockDuration), ClockDuration != 0)
nrowsbefore_outliers <- nrow(RetroDuration_PoT_clean)
RetroDuration_PoT_clean <- RetroDuration_PoT_clean %>%
  group_by(Country,Session) %>%
  mutate(outliers = ClockDuration > Duration_max | ClockDuration < Duration_min) %>%
  filter(!outliers) %>%
  mutate(outliers = find.outliers(ClockDuration,meth = 'trim', probs = probs)) %>%
  filter(!outliers) %>%
  ungroup() %>% select(-outliers)
nrowsafter_outliers <- nrow(RetroDuration_PoT_clean)

cat('Global proportion of outliers', prop_outliers_global <- 1 - nrowsafter_outliers / nrowsbefore_outliers)

save(RetroDuration_PoT_clean, file = file.path(dirBlursday,'RetroDuration_PoT_clean.RData'))

RetroDuration_PoT_clean %>%
  group_by(Country,Session) %>%
  mutate(across(c(ClockDuration), as.numeric)) %>%
  pivot_longer(cols = c(ClockDuration, Passage_of_Time)) %>%
  ggplot(aes(x = value, fill = Country)) + 
  geom_histogram(bins = 50) +
  facet_wrap(~name ,scales = 'free')
```


# panel a
```{r}
load(file = file.path(dirBlursday,'RetroDuration_PoT_clean.RData'))

(fig2a <- RetroDuration_PoT_clean %>%
    group_by(Country,Session) %>%
    ggplot(aes(x = Passage_of_Time, fill = Session)) + 
    geom_histogram(bins = 50)  +
    scale_fill_manual(values = Palette_Session) +
    scale_color_manual(values = Palette_Session) +
    xlab('Passage of Time') +  
    annotate("text", x = -5, y = -60, hjust = 0, vjust = 1, label = 'very\nslow', size = 2) +
    annotate("text", x = 105, y = -60, hjust = 1, vjust = 1, label = 'very\nfast', size = 2) +
    coord_cartesian(xlim = c(0,100), ylim = c(0, 300), clip = "off") + 
    ylab('Count'))

```

## Subjects count

```{r}

RetroDuration_PoT %>% group_by(Country, Session) %>%
  summarize(n = n())


```


# Modeling

```{r}
load(file = file.path(dirBlursday,'RetroDuration_PoT_clean.RData'))

tostat <- RetroDuration_PoT_clean %>% 
  group_by(Country, PID, Session) %>%
  select(Country,PID, Session, Local_Date, Age, Sex, Handedness, ClockDuration, Passage_of_Time) %>%
  filter(Session %in% c('S1','SC')) %>%
  summarize(Local_Date = unique(Local_Date),
            Age = unique(Age),
            Passage_of_Time = unique(Passage_of_Time),
            rPoT = Passage_of_Time / 50) %>%
  add_SubjectiveConfinementIndices() %>%
  add_Mobility() %>%
  add_StringencyIndex() %>%
  add_TimeOfDay() %>%
  mutate(Hour_Of_Day = recode(Hour_Of_Day,`0` = as.integer(24))) %>%
  drop_na(Stringency_Index, Subjective_Confinement)

N <- tostat %>%
  group_by(Session) %>%
  summarize(N = n())

```

## Using lm

```{r}
mylm <- lm(Passage_of_Time ~ Stringency_Index + Mobility_Transit + Subjective_Confinement + Age  +  poly(Hour_Of_Day,3), data = tostat)
summary(mylm)
plot(mylm)
car::Anova(mylm, type = 2)
effectsize::eta_squared(car::Anova(mylm, type = 2))
confint(mylm)

(em <- emmeans(mylm, ~ Subjective_Confinement, at = list(Subjective_Confinement = c(5,20))))
pairs(em)



```
```{r}
library(ordinalCont)

ord_PoT <- ocm(Passage_of_Time ~ Stringency_Index + Mobility_Transit + Subjective_Confinement + Age  +  poly(Hour_Of_Day,3), data = tostat)
summary(ord_PoT)
plot(ord_PoT)

```

# Panel b
```{r}

em <- summary(emmeans(mylm,~ Subjective_Confinement, at = list(Subjective_Confinement = 5:20))) %>%
  mutate(Passage_of_Time = emmean,
         LCL = lower.CL,
         UCL = upper.CL)

(fig2b <- p_SC <- ggplot(tostat %>%
         group_by(Subjective_Confinement) %>%
         mutate(meanPassage_of_Time = mean(Passage_of_Time),
                n = n()),
       aes(x = Subjective_Confinement, y = Passage_of_Time)) +
  geom_jitter(data = tostat, width = .1, col = 'grey', size = .5) +
  geom_line(data = em) +
  # geom_point(col='green',data = em2) +
  geom_ribbon(mapping = aes(ymin = LCL, ymax = UCL),col = NA, alpha = .2,data = em) +
  geom_point(aes(y = meanPassage_of_Time, size = n), col = 'black', show.legend = F) +
    xlab('Subjective Confinement') +
    ylab('Passage of Time') +
    scale_size_area(max_size = 2.5) +
    annotate("text", x = 4, y = -20, hjust = 0, vjust = 1, label = 'feeling\nlonely', size = 2) +
    annotate("text", x = 21, y = -20, hjust = 1, vjust = 1, label = 'not feeling\nlonely', size = 2) +
    annotate("text", y = 5, x = 3.5, hjust = 1, vjust = -1, angle = 90, label = 'very\nslow', size = 2) +
    annotate("text", y = 100, x = 3.5, hjust = 1, vjust = -1, angle = 90, label = 'very\nfast', size = 2) +
    coord_cartesian(xlim = c(5,20),ylim = c(0, 100), clip = "off") 

)
```

# figure 2 final
```{r}

library(patchwork)
fig2a / fig2b + plot_annotation(tag_levels = 'a') & theme(plot.tag = element_text(face = 'bold'))

imagefile = 'PaperFigures/Fig2.pdf'
ggsave(
  basename(imagefile),
  plot = last_plot(),
  device = 'pdf',
  width = 89,
  height = 100,
  path = dirname(imagefile),
  units = 'mm',
  bg = "white"
)

```

