---
title: "Time Social Distancing: Unzipping data"
output: html_notebook
    
---

This document shows how to extract meaningful data from the tables exported by Gorilla with their original file name `data_exp_#####-v#.zip`.

First load useful packages and set root directory  (you may have to `install.packages`).
```{r, message=F}

library(tidyverse)
library(plyr)
library(tools)

# These path and file name need to be changed
rootdir = '/home/maximilien.chaumon/ownCloud/Lab/00-Projects/TimeSocialDistancing/DATA'
datafile <- file.path(rootdir,'data_exp_16303-v2.zip')

tmpdir <- file.path(rootdir,'.tmp')

```

## Unzip data

This is the critical place, where the zip file name should be entered.
```{r}
experimentID <- gsub('.*data_exp_([[:digit:]]+)-v[[:digit:]]+.zip','\\1',datafile)

datadir <- sub('-v[[:digit:]]+.zip','',datafile)

unlink(datadir,recursive=T)

unlink(tmpdir,recursive=T)

unzip(datafile,exdir=tmpdir)
```

## Rename files

We retrieve unique task identifiers: column "questionnaire or task name" from [this google sheet](https://docs.google.com/spreadsheets/d/1Mwy2aGCJ6vSpp4a32NOs83e2H73MQRFUOL_193yb8sQ/edit#gid=0), based on expermient ID (i.e. language) retrieved from [this google sheet]('https://docs.google.com/spreadsheets/d/1p6_WHQXNGFw2EJGny1jb5qivMy2pJ_VRRYoDGRLxgbY/edit#gid=0').

```{r}
library(gsheet)
allnodes <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1Mwy2aGCJ6vSpp4a32NOs83e2H73MQRFUOL_193yb8sQ/edit#gid=0') %>%
  dplyr::rename(order = 1,
                UniqueName = 3) %>%
  filter(order != 'Comment')

experimentIDs <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1p6_WHQXNGFw2EJGny1jb5qivMy2pJ_VRRYoDGRLxgbY/edit#gid=0')

nodekey <- filter(experimentIDs,`Experiment ID` == experimentID)$NodeKey
```

Now that we have these, we know that the current data comes from experiment ``r experimentID`` named ``r nodekey`` in [this google sheet](https://docs.google.com/spreadsheets/d/1Mwy2aGCJ6vSpp4a32NOs83e2H73MQRFUOL_193yb8sQ/edit#gid=0). We can rename all files using these `UniqueName` values stored in the `allnodes` variable.

Here we turn the file names with node codes to `chk-Checkpoint_tsk-TaskName_v-N.csv`, where `Checkpoint` is the last checkpoint passed at the time this task/questionnaire named `TaskName` was passed. Experiment version `N` is also added to the file name.

```{r,warning=F}
fs <- list.files(tmpdir,full.names = T,recursive = T)
dir.create(datadir)

for (f in fs) {
  d <- switch(file_ext(f),
         csv = read_csv(f,col_types = cols()),
         xlsx = readxl::read_excel(f)) %>%
    filter(!is.na(`Task Name`))
  # print(f)
  
  if (nrow(d) == 0) {
    print(paste('No data for', basename(f)))
    file.remove(f)
    next
  }
  
  CurrNode <- filter(allnodes,get(nodekey) == gsub('.*-([[:alnum:]]{4})','\\1',unique(d$`Tree Node Key`)))
  
  if (nrow(CurrNode) == 0 ){
    print(paste('Could not locate task for',basename(f), ':', unique(d$`Task Name`)))
    file.remove(f)
    next
  }

  prevChk <- filter(allnodes,prefix == 'checkpoint',order < CurrNode$order) %>%
    slice(n())
  
  write_csv(d, path = file.path(datadir, paste0('chk-', prevChk$UniqueName, '_tsk-', CurrNode$UniqueName, '_v-', unique(d$`Experiment Version`), '.csv')))
  
  file.remove(f)
}

```

## Merge experiment versions

```{r,message=F}
fs <- list.files(datadir,pattern='chk-(.*)_tsk-(.*)_v-(.*).csv',full.names = T) %>%
  tibble(fname=.) %>%
  extract(fname,into=c('Checkpoint','Task Name','Experiment Version'),'chk-(.*)_tsk-(.*)_v-(.*).csv',remove = F) %>%
  group_by(Checkpoint,`Task Name`) %>%
  group_split()


for (f in fs) {
  chkpt <- unique(f$Checkpoint)
  fn <- unique(f$`Task Name`)
  d <- ldply(as.list(f$fname),read_csv) %>%
    bind_rows() %>%
    arrange(`Experiment Version`)
  write_csv(d, path = file.path(datadir, paste0('chk-',chkpt,'_tsk-',fn,'.csv')))
  file.remove(f$fname)
}
```



