---
title: "Matching PIDs of CA data across sessions"
params:
  Country: CA
  ExperimentName: null
  ExperimentID: null
  Session: null    
output:
  html_document:
    code_folding: hide
    df_print: paged
    toc: yes
  html_notebook:
    code_folding: hide
    df_print: paged
    toc: yes
editor_options: 
  chunk_output_type: inline
---
<!-- # This is the Blursday database paper source code. -->
<!-- # This code was used to prepare the following article: -->
<!-- # XXX Ref. to add XXX -->
<!-- # -->
<!-- # The live application of the server can be accessed at  -->
<!-- # https://dnacombo.shinyapps.io/Blursday/ -->
<!-- # This code is publicly available at -->
<!-- # https://github.com/dnacombo/TSDshiny -->

<!-- #     Copyright (C) 2021  Maximilien Chaumon -->
<!-- # -->
<!-- #     This program is free software: you can redistribute it and/or modify -->
<!-- #     it under the terms of the GNU General Public License as published by -->
<!-- #     the Free Software Foundation, either version 3 of the License, or -->
<!-- #     (at your option) any later version. -->
<!-- # -->
<!-- #     This program is distributed in the hope that it will be useful, -->
<!-- #     but WITHOUT ANY WARRANTY; without even the implied warranty of -->
<!-- #     MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the -->
<!-- #     GNU General Public License for more details. -->
<!-- # -->
<!-- #     You should have received a copy of the GNU General Public License -->
<!-- #     along with this program.  If not, see <http://www.gnu.org/licenses/>. -->


# Match PIDs across sessions


```{r,message=F}
source('helpers.R')
Country = 'CA'
ExperimentName = 'CA-FR'

l <- paramsMatch(Country=Country,experimentIDs = ExperimentIDs)

sessiondatadir <- tibble(fname = list.files(dirData,paste0('data_exp_[^\\.]+Session.*$'),include.dirs = T) ) %>%
  filter(! str_detect(fname,'processed'),
         str_detect(fname,paste0('_',ExperimentName,'_')))


fs <- sapply(sessiondatadir,function(x){list.files(path=file.path(dirData,x),pattern='S._Welcome.csv|S4_ParticipantTracker.csv',full.names = T)})

# initialize empty list
PIDs <- tibble(PubID=character(),email=character(),Session=character(),`Participant Private ID`=character())
# googlesheets4::read_sheet('https://docs.google.com/spreadsheets/d/1CVhBYlWVuL9G48NgWxaIJ-9o5B7YPfrHGE6T2oVgcQA/edit?ts=5faff96a',sheet = Country) %>%
# mutate_all(as.character) %>%
# pivot_longer(cols = starts_with('Session'),names_to = 'Session', values_to = 'Participant Private ID',names_prefix = 'Session') %>%
# filter(!is.na(`Participant Private ID`))

# for each session, we retrieve pubID, privID, and email
for (f in fs) {
  S <- str_match(basename(f),'S(\\d)')[2]
  switch(S,
         '4' = {
           PID <- read_csv(f,col_types = cols(.default = col_character())) %>%
             filter(`Question Key` %in% c('known_participant-text')) %>%
             pivot_wider(id_cols = c(`Participant Private ID`,`Experiment ID`)  ,names_from = `Question Key`, values_from = Response) %>%
             rename(PID = `known_participant-text`) %>% 
             mutate(email = '',
                    Session = S,
                    Country = !!Country,
                    PubID = str_to_lower(PID))
           f <- str_replace(f,'S4_ParticipantTracker.csv','S4_Consent.csv')
           Consent <- read_csv(f,col_types = cols(.default = col_character())) %>%
             filter(`Question Key` %in% c('PID', 'email')) %>%
             pivot_wider(id_cols = c(`Participant Private ID`,`Experiment ID`)  ,names_from = `Question Key`, values_from = Response) %>%
             mutate(Session = S,
                    Country = !!Country,
                    PubID = str_to_lower(PID))
           PID <- bind_rows(Consent,PID) %>%
             distinct(`Participant Private ID`, .keep_all = T)
         },
         {
           PID <- read_csv(f,col_types = cols(.default = col_character())) %>%
             filter(`Question Key` %in% c('PID', 'email')) %>%
             pivot_wider(id_cols = c(`Participant Private ID`,`Experiment ID`)  ,names_from = `Question Key`, values_from = Response) %>%
             mutate(Session = S,
                    Country = !!Country,
                    PubID = str_to_lower(PID))
         }
  )
  
  PIDs <- bind_rows(PIDs,PID) %>%
    # distinct() %>%
    select(`Experiment ID`,	`Country`,	`email`,	`PubID`,everything())
  }

# list all PIDs used. Matching PIDs across sessions are listed together. Attach email.
# Columns: PID, email, Session1, Session2 etc. 
matched_by_PID <- pivot_wider(PIDs, id_cols = PubID, names_from = Session, values_from = `Participant Private ID`, 
                              names_prefix = 'Session',
                              values_fn = function(x){do.call('paste',list(x,collapse = ' '))}) %>%
  left_join(select(PIDs,email,PubID),by='PubID') %>%
  distinct(PubID, .keep_all = T)

# same as above but finding matching emails across sessions.
# Columns: email, Session1, Session2, etc.
matched_by_email <- pivot_wider(PIDs,id_cols = email, names_from = Session, values_from = `Participant Private ID`, 
                                names_prefix = 'Session',
                                values_fn = function(x){do.call('paste',list(x,collapse = ' '))}) %>%
  distinct(email, .keep_all = T)

# list session names
cn <- tibble(cols = colnames(matched_by_PID)) %>% filter(str_detect(cols,'^Session'))

# join the two lists by email
nuPIDs <- right_join(matched_by_PID,
                     matched_by_email,
                     by = 'email') %>%
  distinct(email, .keep_all = T)

# unite all private IDs (matched by email and by PID) in sessions
for (isess in cn$cols) {
  nuPIDs <- nuPIDs %>% 
    unite(col = !!isess,starts_with(isess),sep=' ')
}

# clean up missing values and duplicates, and write to disk
(nuPIDs <- nuPIDs %>%
    mutate_at(.vars = vars(starts_with('Session')),~ str_replace_all(.,'NA ?','')) %>%
    mutate_at(.vars = vars(starts_with('Session')),~ str_trim(str_replace_all(.,'(\\d{7}) (?:\\d{7} ?)*\\1','\\1'))) %>%
    select(PubID,everything()) %>%
  arrange(PubID)%>%
  distinct()
  ) %>%
  select(-email,-PubID) %>%
  distinct() %>%
  write_csv(file.path(datadir,paste0('AllPID_',Country, '.csv')),na='')

```

## count subjects in the Welcome session

```{r}
PIDs %>% group_by(Session) %>%
  summarize(n = n()) %>%
  ggplot(aes(x=Session,y=n,fill=Session,label=n)) +
  geom_col() +
  geom_text(position = position_stack(vjust = 0.5)) +
  ggtitle('Number of participants per session')
```
# Fix PID
Two people have used "julie" as a PubID. We disentangle them here.

```{r echo=TRUE}

patch <- tibble(PubID = c("julie1", "julie2"), Session1 = c("1322710","1420457"), Session4 = "")
(nuPIDs <- nuPIDs %>%
    filter(! Session1 %in% c("1322710","1420457")) %>%
    bind_rows(patch)) %>%
  select(-email,-PubID) %>%
  distinct() %>%
  write_csv(file.path(datadir,paste0("AllPID_",Country, ".csv")),na="")

```

## Find participants who used several email but the same pubID

```{r}
dupem <- nuPIDs %>%
  group_by(PubID) %>%
  filter(n() > 1) %>%
  .$email

matched_by_email %>%
  left_join(select(PIDs,email,PubID),by='email') %>%
filter(email %in% dupem) %>% distinct() %>% select(PubID,email, everything()) %>%arrange(PubID)
```

# find participants who used different pubID but the same email

```{r}
duppid <- nuPIDs %>%
  group_by(email) %>%
  filter(n() > 1) %>%
  .$PubID

matched_by_PID %>% filter(PubID %in% duppid) %>% distinct() %>% select(email, PubID, everything()) %>% arrange(email)
```

# Add PID column to all tasks

Add a PID column to the data, with unique ID for each participant (the first private ID they appear under).

```{r}
suppressWarnings(
  PIDs <- read_csv(file.path(datadir,paste0('AllPID_',Country,'.csv')),col_types = cols()) %>%
    unite('PID',starts_with('Session'),sep=' ',remove=F) %>%
    mutate(PID = str_replace_all(PID,'NA ?',''), # remove NAs
           PID = str_replace(PID,' .*','')) %>%   # discard all but the first PID
    separate(Session1,sprintf('S1_%d',1:5)) %>%
    separate(Session4,sprintf('S4_%d',1:5)) %>%
    pivot_longer(cols = starts_with('S'),values_to = 'origPID') %>%
    filter(!is.na(origPID)) %>%
    select(-name)
)


matchingPIDs <- PIDs$PID
names(matchingPIDs) <- PIDs$origPID

sessiondatadir <- tibble(fname = list.files(dirData,paste0('data_exp_[^\\.]+Session.*$'),include.dirs = T) ) %>%
  filter(! str_detect(fname,'processed'),
         str_detect(fname,paste0('_',ExperimentName,'_')))

fs <- sapply(sessiondatadir,function(x){list.files(path=file.path(dirData,x),pattern='S._.*.csv',full.names = T)})
fs <- fs[!str_detect(fs,'PID.csv')]
fs <- fs[str_detect(fs,'S4')]

for (f in fs) {
  cat(basename(f),sep = '\n')
  Session <- str_match(basename(f),'S(\\d)')[2]
  
  read_csv(f,col_types = cols(.default = col_character())) %>%
    mutate(PID = recode(`Participant Private ID`,!!!matchingPIDs)) %>%
    write_csv(f)
}
```

