---
title: "Matching PIDs of AR data across sessions"
params:
  Country: AR
  ExperimentName: null
  ExperimentID: null
  Session: null    
output:
  html_document:
    code_folding: hide
    df_print: paged
    toc: yes
  html_notebook:
    code_folding: hide
    df_print: paged
    toc: yes
---


# Match PIDs across sessions


```{r,message=F}
source('helpers.R')
Country = 'AR'

l <- paramsMatch(Country=Country,experimentIDs = ExperimentIDs)

sessiondatadir <- tibble(fname = list.files(dirData,paste0('data_exp_[^\\.]+Session.*$'),include.dirs = T) ) %>%
  filter(! str_detect(fname,'processed'),
         str_detect(fname,paste0('_',Country,'_')))


fs <- sapply(sessiondatadir,function(x){list.files(path=file.path(dirData,x),pattern='S._Welcome.csv',full.names = T)})

# initialize empty list
PIDs <- tibble(PubID=character(),email=character(),Session=character(),`Participant Private ID`=character())
# googlesheets4::read_sheet('https://docs.google.com/spreadsheets/d/1CVhBYlWVuL9G48NgWxaIJ-9o5B7YPfrHGE6T2oVgcQA/edit?ts=5faff96a',sheet = Country) %>%
# mutate_all(as.character) %>%
# pivot_longer(cols = starts_with('Session'),names_to = 'Session', values_to = 'Participant Private ID',names_prefix = 'Session') %>%
# filter(!is.na(`Participant Private ID`))

# for each session, we retrieve pubID, privID, and email
for (f in fs) {
  S <- str_match(basename(f),'S(\\d)')[2]
  PID <- read_csv(f,col_types = cols(.default = col_character())) %>%
    filter(`Question Key` %in% c('PID', 'email')) %>%
    pivot_wider(id_cols = c(`Participant Private ID`,`Experiment ID`)  ,names_from = `Question Key`, values_from = Response) %>%
    mutate(Session = S,
           Country = !!Country,
           PubID = str_to_lower(PID))
  
  
  PIDs <- bind_rows(PIDs,PID) %>%
    # distinct() %>%
    select(`Experiment ID`,	`Country`,	`email`,	`PubID`,everything())
}

# list all PIDs used. Matching PIDs across sessions are listed together. Attach email.
# Columns: PID, email, Session1, Session2 etc. 
matched_by_PID <- pivot_wider(PIDs,id_cols = PubID,names_from = `Experiment ID`,values_from = `Participant Private ID`, 
                              values_fn = function(x){do.call('paste',list(x,collapse = ' '))}) %>%
  left_join(select(PIDs,email,PubID),by='PubID') %>%
  distinct()

# same as above but finding matching emails across sessions.
# Columns: email, Session1, Session2, etc.
matched_by_email <- pivot_wider(PIDs,id_cols = email,names_from = `Experiment ID`,values_from = `Participant Private ID`, 
                                values_fn = function(x){do.call('paste',list(x,collapse = ' '))}) %>%
  distinct()

# list session names
cn <- tibble(cols = colnames(matched_by_PID)) %>% filter(str_detect(cols,'\\d{5}'))

# join the two lists by email
nuPIDs <- right_join(matched_by_PID,
                      matched_by_email,
                      by = 'email') %>%
    distinct()

# unite all private IDs (matched by email and by PID) in sessions
for (isess in cn$cols) {
  nuPIDs <- nuPIDs %>% 
    unite(col = !!isess,starts_with(isess),sep=' ')
}

# clean up missing values and duplicates, and write to disk
(nuPIDs <- nuPIDs %>%
    mutate(across(matches('^\\d{5}$'),~ str_replace_all(.,'NA ?',''))) %>%
    mutate(across(matches('^\\d{5}$'),~ str_trim(str_replace_all(.,'(\\d{7}) (?:\\d{7} ?)*\\1','\\1')))) %>%
    select(PubID,everything()) %>%
  arrange(PubID)%>%
  distinct()) %>%
  select(-email,-PubID) %>%
  distinct() %>%
  write_csv(file.path(datadir,paste0('AllPID_',Country, '.csv')),na='')

```

## count subjects in the Welcome session

```{r}
PIDs %>% group_by(`Experiment ID`) %>%
  summarize(n = n()) %>%
  ggplot(aes(x=`Experiment ID`,y=n,fill=`Experiment ID`,label=n)) +
  geom_col() +
  geom_text(position = position_stack(vjust = 0.5)) +
  ggtitle('Number of participants per Experiment ID')
```

## Find participants who used several email but the same pubID

```{r}
dupem <- nuPIDs %>%
  group_by(PubID) %>%
  filter(n() > 1) %>%
  .$email

matched_by_email %>%
  left_join(select(PIDs,email,PubID),by='email') %>%
filter(email %in% dupem) %>% distinct() %>% select(PubID,email, everything()) %>%arrange(PubID)
```

# find participants who used different pubID but the same email

```{r}
duppid <- nuPIDs %>%
  group_by(email) %>%
  filter(n() > 1) %>%
  .$PubID

matched_by_PID %>% filter(PubID %in% duppid) %>% distinct() %>% select(email, PubID, everything()) %>% arrange(email)
```
# Fix PID

One subject seems to have entered two different PubIDs: `matt` and `matias` but same email `mati_182@hotmail.com`. We rename it `matt`.
Also subject who used email `sol.brizuela@live.com.ar` used two pubIDs `s12` and `sb`. We merge it.
**Note:** It is also possible that two people used the same email address. Keep this in mind if one subject seems to have run twice as many trials in all tasks?
```{r echo=TRUE}

patch <- tibble(email = "mati_182@hotmail.com",	`20044` = "",	`19856` = "",	`19880` = "",	`19904` = "", `17423` = "1396062 1495635", PubID = 'matt') %>%
  bind_rows(tibble(email = "sol.brizuela@live.com.ar",	`20044` = "",	`19856` = "",	`19880` = "",	`19904` = "", `17423` = "1391538 1921583", PubID = 'sb'))
(nuPIDs <- nuPIDs %>% filter(! email %in% c('mati_182@hotmail.com', 'sol.brizuela@live.com.ar')) %>%
  bind_rows(patch)) %>%
  select(-email,-PubID) %>%
  distinct() %>%
  write_csv(file.path(datadir,paste0('AllPID_',ExperimentName[1], '.csv')),na='')

```

# Add PID column to all tasks

Add a PID column to the data, with unique ID for each participant (the first private ID they appear under).

```{r}

suppressWarnings(
  PIDs <- read_csv(file.path(datadir,paste0('AllPID_',Country,'.csv')),col_types = cols()) %>%
    unite('PID',matches('^\\d{5}$'),sep=' ',remove=F) %>%
    mutate(PID = str_replace_all(PID,'NA ?',''), # remove NAs
           PID = str_replace(PID,' .*','')) %>%   # discard all but the first PID
    separate(`17423`,sprintf('1_%d',1:5)) %>%
    separate(`20044`,sprintf('2_%d',1:5)) %>%
    separate(`19856`,sprintf('3_%d',1:5)) %>%
    separate(`19880`,sprintf('4_%d',1:5)) %>%
    separate(`19904`,sprintf('5_%d',1:5)) %>%
    pivot_longer(cols = matches('\\d_.*'),values_to = 'origPID') %>%
    filter(!is.na(origPID)) %>%
    select(-name)
)


matchingPIDs <- PIDs$PID
names(matchingPIDs) <- PIDs$origPID

sessiondatadir <- tibble(fname = list.files(datadir,paste0('data_exp_[^\\.]+Session[0-9]+$'),include.dirs = T) ) %>%
  filter(! str_detect(fname,'processed'),
         str_detect(fname,Country))

fs <- sapply(sessiondatadir,function(x){list.files(path=file.path(datadir,x),pattern='S._.*.csv',full.names = T)})
fs <- fs[!str_detect(fs,'PID.csv')]

for (f in fs) {
  cat(basename(f),sep = '\n')
  Session <- str_match(basename(f),'S(\\d)')[2]
  
  read_csv(f,col_types = cols(.default = col_character())) %>%
    mutate(PID = recode(`Participant Private ID`,!!!matchingPIDs)) %>%
    write_csv(f)
}
```

