---
title: "Data all sessions, TR data"
params:
  ExperimentName: TR
  rootdir: '/home/maximilien.chaumon/ownCloud/Lab/00-Projects/TimeSocialDistancing/DATA'
output:
  html_notebook:
    code_folding: hide
    df_print: paged
    toc: yes
  html_document:
    code_folding: hide
    df_print: paged
    toc: yes
---


# Match PIDs across sessions


```{r,message=F}
library(tidyverse)
source('helpers.R')

datadir <- tibble(fname = list.files(params$rootdir,paste0('data_exp_[^\\.]+Session[0-9]+$'),include.dirs = T) ) %>%
  filter(! str_detect(fname,'processed'),
         str_detect(fname,ExperimentName))


```

## Collect, match, and save PIDs across sessions
```{r}
fs <- sapply(datadir,function(x){list.files(path=file.path(params$rootdir,x),pattern='S._Welcome.csv',full.names = T)})

# initialize empty list
PIDs <- tibble(PID=character(),email=character(),Session=character(),`Participant Private ID`=character())
# googlesheets4::read_sheet('https://docs.google.com/spreadsheets/d/1CVhBYlWVuL9G48NgWxaIJ-9o5B7YPfrHGE6T2oVgcQA/edit?ts=5faff96a',sheet = ExperimentName) %>%
# mutate_all(as.character) %>%
# pivot_longer(cols = starts_with('Session'),names_to = 'Session', values_to = 'Participant Private ID',names_prefix = 'Session') %>%
# filter(!is.na(`Participant Private ID`))

# for each session, we retrieve pubID, privID, and email
for (f in fs) {
  Session <- str_match(basename(f),'S(\\d)')[2]
  PID <- read_csv(f,col_types = cols(.default = col_character())) %>%
    filter(`Question Key` %in% c('PID', 'email')) %>%
    pivot_wider(id_cols = c(`Participant Private ID`,`Experiment ID`)  ,names_from = `Question Key`, values_from = Response) %>%
    mutate(Session = Session,
           ExperimentName = ExperimentName,
           PID = str_to_lower(PID))
  
  
  PIDs <- bind_rows(PIDs,PID) %>%
    distinct() %>%
    select(`Experiment ID`,	`ExperimentName`,	`email`,	`PID`,everything())
}

# list all PIDs used. Matching PIDs across sessions are listed together. Attach email.
# Columns: PID, email, Session1, Session2 etc. 
matched_by_PID <- pivot_wider(PIDs,id_cols = PID,names_from = Session,values_from = `Participant Private ID`, 
                              names_prefix = 'Session',
                              values_fn = function(x){do.call('paste',list(x,collapse = ' '))}) %>%
  left_join(select(PIDs,email,PID),by='PID')

# same as above but finding matching emails across sessions.
# Columns: email, Session1, Session2, etc.
matched_by_email <- pivot_wider(PIDs,id_cols = email,names_from = Session,values_from = `Participant Private ID`, 
                                names_prefix = 'Session',
                                values_fn = function(x){do.call('paste',list(x,collapse = ' '))})

# list session names
cn <- tibble(cols = colnames(matched_by_PID)) %>% filter(str_detect(cols,'^Session'))

# join the two lists by email
nuPIDs <- right_join(matched_by_PID,
                      matched_by_email,
                      by = 'email') %>%
    distinct()

# unite all private IDs (matched by email and by PID) in sessions
for (isess in cn$cols) {
  nuPIDs <- nuPIDs %>% 
    unite(col = !!isess,starts_with(isess),sep=' ')
}

# clean up missing values and duplicates, and write to disk
(nuPIDs <- nuPIDs %>%
    mutate_at(.vars = vars(starts_with('Session')),~ str_replace_all(.,'NA ?','')) %>%
    mutate_at(.vars = vars(starts_with('Session')),~ str_trim(str_replace_all(.,'(\\d{7}) (?:\\d{7} ?)*\\1','\\1'))) %>%
    select(PID,everything()) %>%
  arrange(PID)%>%
  distinct()) %>%
  select(-email,-PID) %>%
  distinct() %>%
  write_csv(file.path(params$rootdir,paste0('AllPID_',ExperimentName[1], '.csv')),na='')

(nuPIDs)
```
## count subjects
```{r}
options(dplyr.summarise.inform=F)
PIDs %>% group_by(Session) %>%
  summarize(n = n()) %>%
  ggplot(aes(x=Session,y=n,fill=Session,label=n)) +
  geom_col() +
  geom_text(position = position_stack(vjust = 0.5)) +
  ggtitle('Number of participants per session')
```

## Find participants who used several email addresses

```{r}
dupem <- nuPIDs %>%
  group_by(PID) %>%
  filter(n() > 1) %>%
  .$email

matched_by_email %>%
  left_join(select(PIDs,email,PID),by='email') %>%
filter(email %in% dupem) %>% distinct() %>% select(PID,email, everything()) %>%arrange(PID)
```
The participants above will not be processed automatically correctly. We fix them by hand here.

```{r}

patch <- read_tsv("123456	acaliskan127@gmail.com	1303562	1596049
123456	mozsan17@ku.edu.tr	1309372	NA
123456	serdal@ku.edu.tr	1370548	NA
123456	nkapoglu17@ku.edu.tr	1425546	1916408
123456	fyardimci17@ku.edu.tr	1454132	NA",col_names = c('PID', 'email', 'Session1', 'Session2'),col_types=cols(.default=col_character()))

(nuPIDs <- nuPIDs %>% filter(! email %in% dupem) %>%
  bind_rows(patch)) %>%
  select(-email,-PID) %>%
  distinct() %>%
  write_csv(file.path(params$rootdir,paste0('AllPID_',ExperimentName[1], '.csv')),na='')

```

# find participants who used different pubID
```{r}
duppid <- nuPIDs %>%
  group_by(email) %>%
  filter(n() > 1) %>%
  .$PID

matched_by_PID %>% filter(PID %in% duppid) %>% distinct() %>% select(email, PID, everything()) %>% arrange(email)
```

# Match IDs across sessions.

Add a PID column to the data, with unique ID for each participant (the first private ID they appear under).

```{r}

suppressWarnings(
  PIDs <- nuPIDs %>% select(-PID,-email) %>% distinct() %>%
  unite('PID',starts_with('Session'),sep=' ',remove=F) %>%
  mutate(PID = str_replace_all(PID,'NA ?',''), # remove NAs
         PID = str_replace(PID,' .*','')) %>%   # discard all but the first PID
  separate(Session1,sprintf('S1_%d',1:5)) %>%
  separate(Session2,sprintf('S2_%d',1:5)) %>%
  pivot_longer(cols = starts_with('S'),values_to = 'origPID') %>%
  filter(!is.na(origPID)) %>%
  select(-name) %>%
    filter(origPID != "")
)


matchingPIDs <- PIDs$PID
names(matchingPIDs) <- PIDs$origPID

datadir <- tibble(fname = list.files(params$rootdir,paste0('data_exp_[^\\.]+Session[0-9]+$'),include.dirs = T) ) %>%
  filter(! str_detect(fname,'processed'),
         str_detect(fname,ExperimentName))

fs <- sapply(datadir,function(x){list.files(path=file.path(params$rootdir,x),pattern='S._.*.csv',full.names = T)})
fs <- fs[!str_detect(fs,'PID.csv')]

for (f in fs) {
  print(f)
  Session <- str_match(basename(f),'S(\\d)')[2]
  read_csv(f,col_types = cols(.default = col_character())) %>%
    mutate(PID = recode(`Participant Private ID`,!!!matchingPIDs)) %>%
    write_csv(f)
}
```

