---
title: "Time Social Distancing: Shaping data"
output: html_notebook
    
---


This document explains how to extract meaningful data from the tables exported by Gorilla.

First load useful packages and set root directory  (you may have to `install.packages`).
```{r, message=F}

library(tidyverse)
library(plyr)
library(tools)

datadir = '/home/maximilien.chaumon/ownCloud/Lab/00-Projects/TimeSocialDistancing/MOCK_DATA'

tmpdir <- file.path(datadir,'.tmp')

```

# Retrieve data from zip file

If you download experiment data from Gorilla, you probably want to get it in zip format, and extract it with this code chunk.

```{r, warning=F}

datafile <- file.path(datadir,'data_exp_15575-v41.zip')
# datafile <- file.path(datadir,'VVW_data_exp_15096-v35.zip')
# datafile = file.path(datadir,'drive-download-20200426T134951Z-001.zip')

datadir <- sub('.zip','',datafile)

suppressWarnings(dir.create(datadir))

dum <- file.remove(list.files(tmpdir,full.names = T))

unzip(datafile,exdir=tmpdir)

fs <- list.files(tmpdir,full.names = T)

for (f in fs) {
  d <- switch(file_ext(f),
         csv = read_csv(f,col_types = cols()),
         xlsx = readxl::read_excel(f)) %>%
    filter(!is.na(`Task Name`))
  
  if (nrow(d) == 0) {
    print(paste('No data for', basename(f)))
    file.remove(f)
    next
  }
  
  fn <- unique(d$`Task Name`) %>%
    gsub(' ','_',.,)
  
  write_csv(d, path = file.path(datadir, paste0(fn,'.csv')))
  
  file.remove(f)
}

```
# Tasks

## Implicit Timing DE

```{r, message=F}

datafile <- file.path(datadir,'ImplicitTiming-DE.csv')

orig <- read_csv(datafile)

data_in_shape <- orig %>%
  select(`Zone Type`, display,`Participant Private ID`,`Schedule ID`, `Local Date`,
         `Trial Number`,`Reaction Time`,SOA,condition) %>%
  filter(display == 'trial',`Zone Type` == 'response_keyboard_single') %>%
  select(-`Zone Type`,-display) %>%
  mutate(SOA = as.numeric(SOA),
         condition = factor(condition,levels=c(0,1),labels=c('nonPred','Pred')),
         RTE = filter(orig,display == 'fin',`Zone Type` == 'response_text_entry')$Response)


ggplot(data_in_shape, aes(x=SOA,y=`Reaction Time`,col=condition,group=interaction(condition,SOA))) +
  geom_boxplot()


```

```{r}
datafile <- file.path(datadir,'1back-EN-DE.csv')

orig <- read_csv(datafile)

processed <- orig %>%
  select(`Zone Type`, display,`Participant Private ID`,`Schedule ID`, `Local Date`,
         `Trial Number`,`Reaction Time`, Attempt,Correct, letters, ILI
  ) %>%
  filter(display == 'block1back',`Zone Type` == 'response_keyboard') %>%
  select(-`Zone Type`,-display) %>%
  mutate(letters = gsub('<.*?>','',letters),
         back_1 = tolower(letters) == lag(tolower(letters),default='firstTrial'))

processed2 <- orig %>%
  select(`Zone Type`, display,`Participant Private ID`,`Schedule ID`, `Local Date`,
         `Trial Number`,`Reaction Time`, Attempt,Correct, letters, Response
  ) %>%
  filter(display == 'block1back_end',`Zone Type` == 'response_text_entry') %>%
  select(-`Zone Type`,-display) %>%
  separate(Response,c('m','s')) %>% mutate_at(.vars=c('m','s'),.funs = function(x){ifelse(is.na(x),0,x)}) %>%
  mutate(Duration = sum(as.numeric(s) + 60 * as.numeric(m))) %>%
  select(-m,-s)

processed3 <- orig %>%
  select(`Zone Type`, display,`Participant Private ID`,`Schedule ID`, `Local Date`,
         `Trial Number`,`Reaction Time`, Attempt,Correct, letters, Response
  ) %>%
  filter(display == 'block1back_end',`Zone Type` == 'response_rating_scale_likert') %>%
  select(-`Zone Type`,-display) %>%
  mutate(DurationLikertRating = Response)
  
processed <- left_join(processed,processed2) %>%
  left_join(processed3)

rm(processed2,processed3)
  
ggplot(processed,aes(x=back_1,y=`Reaction Time`)) +
  geom_jitter()

```

# Questionnaires

## BFI 10

```{r, message=F}

datafile <- file.path(datadir,'09_BFI-10-DE.csv')

orig <- read_csv(datafile)

data_in_shape <- orig %>%
  select(`Participant Private ID`,`Schedule ID`, `Local Date`,
         `Question Key`, Response) %>%
  filter(grepl('-quantised',x=`Question Key`)) %>%
  mutate(`Question Key` = str_replace(`Question Key`,"BFI-10_([0-9]+)-quantised",'Q\\1'),
         Response = as.numeric(Response)) %>%
  pivot_wider(names_from = `Question Key`,values_from = Response) %>%
  mutate(Extraversion      = ((6 - Q1) + Q6) /2,
         Agreableness      = ((6 - Q7) + Q2) /2,
         Conscientiousness = ((6 - Q3) + Q8) /2,
         Neuroticism       = ((6 - Q4) + Q9) /2,
         Openness          = ((6 - Q5) + Q10) /2) %>%
  select(-starts_with('Q'))

toplot <- data_in_shape %>%
  pivot_longer(cols=c(Extraversion,Agreableness,Conscientiousness,Neuroticism,Openness),names_to = 'BigFive',values_to = 'Value')

  ggplot(toplot, aes(x=BigFive,y=Value,col=BigFive)) +
  geom_point()
  
```

## FMI – Freiburg Mindfulness Questionnaire (German: FFA)
Rarely = 1
Occasionally = 2
Fairly often = 3
Almost always = 4

Sum score of 14 items
Only item 13 = reversed-scored


```{r, message=F}
datafile <- file.path(datadir,'13_FFA-EN-DE.csv')

orig <- read_csv(datafile)

data_in_shape <- orig %>%
  select(`Participant Private ID`,`Schedule ID`, `Local Date`,
         `Question Key`, Response) %>%
  filter(grepl('-quantised',x=`Question Key`)) %>%
  mutate(`Question Key` = str_replace(`Question Key`,"FFA_([0-9]+)-quantised",'Q\\1'),
         Response = as.numeric(Response)) %>%
  pivot_wider(names_from = `Question Key`,values_from = Response) %>%
  mutate(FMI      = Q1+Q2+Q3+Q4+Q5+Q6+Q7+Q8+Q9+Q10+Q11+Q12+(5-Q13)+Q14
         ) %>%
  select(-starts_with('Q'))

(toplot <- data_in_shape %>%
  pivot_longer(cols=c(FMI),names_to = 'Score',values_to = 'Value'))


  
```


## CFC-14 – Consideration of Future Consequences -14
1 = very uncharacteristic of me
2 = characteristic of me
3 = (not labelled)
4 = neither nor
5 = (not labelled)
6 = characteristic of me
7 = very characteristic of me

CFC-F (Future): = Summe (items 1, 2, 6, 7, 8, 13, 14)
CFC-I (Immediate) = Summe (items 3, 4, 5, 9, 10, 11, 12)
CFC_sumscore = CFC-F + (56-CFC-I) 

```{r}


```

