# Tapping and TapVis data
BLURSDAY DATABASE
Analysis and code: Ignacio Spiousas and Rodrigo Laje

(Might take a long time to run because of the size of the TapVis data)


Directory structure:

`$WDIR/Data_analysis/code/`
`tapping_aux_functions.R`

`$WDIR/Data_analysis/paper/`
`Tapping_figure.R`
`TapVis_figure.R`

`$WDIR/Data_analysis/data/`
`data-Tapping_{$COUNTRY}_{$DATE}.RData`
`data-TapVis_{$COUNTRY}_{$DATE}.RData` 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)
```

```{r}
pacman::p_load(tidyverse, ggdist, ggpubr, rcartocolor, ggtext, patchwork, here, 
               countrycode, janitor, Routliers, colorspace, pracma, mclust, lme4, patchwork)

source(here('code/tapping_aux_functions.R'))
source(here('paper/Tapping_figure.R'))
source(here('paper/TapVis_figure.R'))

fig_paper <- fig_paper_free_tapping | fig_paper_synchronization | fig_paper_continuation
fig_paper

ggsave(here('paper/fig_paper.png'), dpi = 300, width = 15, height = 15, units = "cm")
ggsave(here('paper/fig_paper.pdf'), width = 15, height = 15, units = "cm")
ggsave(here('paper/fig_paper.eps'), width = 15, height = 15, units = "cm")

```

