---
title: "Extracting data for Task Implicit Timing"
params:
  experimentID: [15096,16303]
  rootdir: /home/maximilien.chaumon/ownCloud/Lab/00-Projects/TimeSocialDistancing/DATA
output:
  html_document:
    df_print: paged
    toc: yes
  html_notebook:
    code_folding: hide
    toc: yes
---


```{r, message=F}
library(tidyverse)
library(ggbeeswarm)
source('helpers.R')
```

```{r, message=F}

datadir = file.path(params$rootdir,paste0('data_exp_', paste(params$experimentID,collapse='-'), '_', ExperimentName[1]))
outdir = paste(datadir,'processed',sep='_')
dir.create(outdir,showWarnings = F)

experimentID <- params$experimentID

datafiles <- list.files(datadir,'S1_Implicit_r.*.csv',full.names = T)

tmpdir <- file.path(params$rootdir,'.tmp')
unlink(tmpdir,recursive=T)

if (is_empty(datafiles)){
  print('No Implicit data')
  knitr::knit_exit()
  }

```

### Read and describe data

```{r, warning=F}

orig <- T_read(datafiles) %>%
  mutate(Run = as.factor(str_replace(File,'S._Implicit_r(.).csv','\\1')),
         `Reaction Time` = as.numeric(`Reaction Time`))

N <- T_Nsuj(orig)


```

Number of participants who completed this task:
`r N`

```{r}

T_Complete(orig)

```

### Extracting data

```{r}

(data_in_shape <- orig %>%
  filter(display == 'trial',`Zone Type` == 'response_keyboard_single') %>%
  mutate(SOA = factor(SOA,levels=c('500','1750','3000')),
         condition = factor(condition,levels=c(0,1),labels=c('nonPred','Pred'))) %>%
  select(`Participant Private ID`,`Local Date`,
         SOA,condition,Run,`Reaction Time`,`Task Version`, `Experiment ID`)) %>%
  write_csv(file.path(outdir,'S1_ImplicitTiming.csv'))
```


```{r}
ggplot(data_in_shape,aes(x=SOA,y=`Reaction Time`,col=condition,group=interaction(condition,SOA))) +
  geom_boxplot()
```

Lots of NA values for condition. What happened?

```{r}
data_in_shape %>% filter(is.na(condition)) %>% group_by(`Participant Private ID`) %>%
  summarize(n = n(),
            version = first(`Task Version`),
            ExperimentID = first(`Experiment ID`))
```

These are the problematic subjects. All from task version 5 ExperimentID 15096.
We discard them for now. We could retrieve condition by looking at blocks of 9 trials and checking whether or not the SOA is constant (condition==1 Pred), or variable (condition = 0 non PRed).


```{r}

data_in_shape <- filter(data_in_shape,!is.na(condition))


ggplot(data_in_shape,aes(x=SOA,y=`Reaction Time`,col=condition,group=interaction(condition,SOA))) +
  geom_boxplot()

```


```{r}
data_in_shape %>% 
  group_by(`Participant Private ID`, condition, SOA) %>%
  summarize(meanRT = mean(`Reaction Time`)) %>%
  group_by(condition, SOA) %>%
  summarize(n = n(),
            semRT = sd(meanRT) / sqrt(n),
            meanRT = mean(meanRT)) %>%
  ggplot(aes(x=SOA,y=meanRT,col=condition,group=interaction(condition,SOA),ymin = meanRT - semRT, ymax = meanRT + semRT)) +
  geom_pointrange()

```

```{r}
library(lme4)
library(lmerTest)
library(emmeans)

m <- lmer(log10(`Reaction Time`) ~ condition * SOA + (1 | `Participant Private ID`), data_in_shape )

anova(m)

em <- summary(emmeans(m,specs = ~ condition + SOA),type = 'response',bias.adj = T)

data_in_shape %>% 
  group_by(`Participant Private ID`, condition, SOA) %>%
  summarize(meanRT = mean(`Reaction Time`)) %>%
  group_by(condition, SOA) %>%
  summarize(n = n(),
            semRT = sd(meanRT) / sqrt(n),
            meanRT = mean(meanRT)) %>%
ggplot(aes(x=SOA,y=meanRT,col=condition,group=interaction(condition,SOA),ymin = meanRT - semRT, ymax = meanRT + semRT)) +
  geom_pointrange() +
  geom_pointrange(data = em, aes(y=response,ymin = asymp.LCL, ymax = asymp.UCL),shape = 2)

```




